\chapter{First Story}

Author: DrowningDream

\enquote{Pizza?  I didn't think there'd be pizza in heaven,} Jim said.\\

\enquote{Why not?  Pizza is the shit,} the angel said.\\



\enquote{And cursing.  And beer?  Is that beer?}\\



In fact, the table was laid out with all the things Jim loved.  Chicken wings, malt whiskey, chilly fries, club sandwiches, those little wieners wrapped in bacon.  Over the table hung a cage where two beautiful women danced naked to 90's alternative.  The angel saw him gazing.\\



\enquote{You can have them after dinner,} he said.  \\



\enquote{Are they being punished?} Jim asked.  He was a man, through and through, but he didn't like the idea of raping someone in paradise.\\



\enquote{Punished?  Is that what you think we do here?  They love it.  Some women like to party.  We don't hold that against them.  Cherry there has been welcoming our new guests for two hundred years.}  The angel leaned close with a knowing smile.  \enquote{There are no anal fissures in heaven, so go wild.}\\



Jim coughed.  \enquote{So uh, well . . .}  He coughed again.  \enquote{What are the uh, ground rules?}\\



\enquote{Ground rules?}\\



\enquote{Like, what's the forbidden fruit?  What's the catch around here?}\\



\enquote{No catches.  The boss doesn't care for rules.  Everybody gets in, and everybody gets what they desire.  Let's say you were a Christian all your life, well I'd be all shiny and I'd take you on the holy tour, you'd get to look down at hell and pity the damned, that sort of thing.  If you're Jim from Tennessee, you get chicken wings and bitches.}\\



\enquote{Huh,} Jim said.  \enquote{You know, I never really believed in this place, but I figured, if it was there, it'd be a little more uptight.}\\



\enquote{Not since Lucy reclaimed the throne.}\\



\enquote{Lucy?}\\



\enquote{Lucifer.  He's Lucy now.  Or she's Lucy now.  We're all a little confused.  But hey, more power to him if that's what gets her off.}\\



\enquote{Lucifer?!  Lucifer is in charge of heaven?}\\



Jim knocked over his beer in surprise.  The angel was laughing heartily.  \\



\enquote{Oh, the shock on your faces, it never gets old!  Yes, Lucifer fought a last resistance a very long time ago.  He crushed the Usurper handily.  As the Usurper fell, he passed through earth, and it was in retaliation that he saddled you guys with all those ridiculous books and laws.}\\



\enquote{No shit.}\\



\enquote{No shit.}\\

%%%%
\asterism

Jim pulled out from long years of habit.  To his surprise, he orgasmed a slice of apple pie, complete with a fork and a dapple of cream.\\



\enquote{Sorry,} Cherry said.  She took a bite and melted with satisfaction.  \enquote{I really love pie after sex.}\\



\enquote{No, that was awesome.}  Jim was looking in awe at his penis.  In Tennessee, whatever came out of it was generally a nuisance.  It certainly hadn't been pie.\\



Cherry laughed.  \enquote{It takes a little getting used to.}\\



\enquote{Yeah, I guess it does.}\\



He lay down on his back with his hands clasped behind his head.  While Cherry enjoyed her dessert, he tried to bring the last several hours into focus.\\



\enquote{So, you heard the angel and me talking, right?}\\



\enquote{Sure.}\\



\enquote{About Lucy and the resistance and all that?}\\



\enquote{Yeah.}\\



\enquote{Is that what he told you?}\\



\enquote{What do you mean?}\\



Jim had never given these sorts of things much thought, so he had difficulty articulating the funny feeling in his brain.  He looked at Cherry's breasts, ran a finger down her back, watched her eat the pie.  Paradise . . .\\



\enquote{I mean, if part of this place is hearing what you want to hear, how do you know what's what?  How do we know what's true?}\\



Cherry swallowed and shook her fork.  \enquote{Oh yeah, the paradox thingy.  You know, it's been a long time since I thought about it.  You're pretty quick to grab it so fast.  It'll bother you for a while, but when you get to live the way you want to live the whole truth thing just kind of goes out the window.  I mean, who cares?}\\



\enquote{But, what if what you want is the truth?  Like, is there a \textit{truth}?}\\



She held up the pie.  \enquote{This is the fucking truth, honey.}  The way she said it, he found difficulty finding any fault with it.  Still, he was bothered, and he didn't think a person should feel bothered in heaven.  \\



\enquote{What if this is really hell?  What if somebody really is looking down, pitying us?} he wondered aloud.\\

%%%%

\asterism

The walls began to shake.\\



\enquote{Wow, that really must be bothering you,} Cherry said.\\



\enquote{What?  Why?  What's happening?}  Jim was on his feet now.  \enquote{Is this bad?}\\



\enquote{Lucy's coming.  She comes around when the paradox gets to you.  Don't worry, she's super nice.  Tell her you like her dress.}\\



\enquote{What?}\\



There was a warbling, pixelating \textit{whoomf}
 and a beautiful woman stepped out of a hole in the wall.  When the hole closed, the room shuddered back to solid.\\



\enquote{Cherry!} the woman exclaimed.  \enquote{You indigo slut, it's been ages!  How are you!}\\



The two of them hugged.  Jim stood naked and speechless.\\



\enquote{This is Jim,} Cherry said, after a few more obligatory exchanges.  "He's worried about the whole \textit{where am I}
 thing."\\



\enquote{Jim.}  Lucy held out her hand.  The nails were painted, the fingers were milk white.\\



\enquote{I - I like your dress,} Jim said.\\



Lucy's laughter was sudden, honest, and contagious.  Soon all three of them were laughing.  Jim began to feel embarrassed he had been taking things so seriously.\\



\enquote{Well, I do hate these formalities,} Lucy said, drawing a card from her blouse, \enquote{but there is bureaucracy even here.}  She handed him the card.  \enquote{If you ever want to know the truth, just find the address on the card there.  They'll fill you in on everything.}\\



\enquote{Really?} Jim said, taken aback.  \enquote{Just like that?}\\



\enquote{Well . . .}\\



Aha!  Jim's head rejoiced.  A catch!  Finally a damn catch.  It eased his mind immensely just knowing there was something up.\\



\enquote{If you go to the truth, you can't come back.}  Lucy's frown was sexual.  Everything about her was sexual.\\



\enquote{You can't come back?  Why?}\\



\enquote{I can't tell you that.  It's part of the truth.}\\



Jim looked at the card.  It was nothing but TRUTH in capital letters, under which read the enticing address, 1 Truth Road.\\



Lucy's hand was on his arm.  He hadn't noticed her approach.  When he looked up there was intensity in her eyes.  It thrilled him.  She spoke softly.\\



\enquote{My advice is always the same.  You have an eternity to enjoy yourself.  The truth can wait.}\\



He was in her mouth before he knew what was happening.  It was pleasure beyond anything he'd ever known.  When he finished, and Lucy took her leave, he and Cherry shared the bucket of chicken wings.\\

\asterism

It took Jim 376 years to get bored.  He stood at 1 Truth Road, thinking it was funny how small the building was.\\



When he walked in, the man behind the reception desk smiled.\\



\enquote{You seek the truth?}  the man said.\\



\enquote{I suppose I do,} Jim said.\\



\enquote{If you don't mind, there's a series of questions I'd like to ask you.  This is completely optional, but your honest answers help us improve paradise.}\\



Jim shrugged.  \enquote{Shoot.}\\



\enquote{How would you rate your overall experience?  These are all one to ten, by the way.}\\



\enquote{Ten.}\\



\enquote{How helpful was our staff?}\\



\enquote{Ten.}\\



\enquote{The weather?}\\



\enquote{Ten.}\\



\enquote{The event center?}\\



\enquote{Ten.}\\



\enquote{The wi-fi?}\\



\enquote{You know what, just put me down for ten on everything.}\\



The man nodded knowingly.  It took him a good five minutes to fill in all the tens, and Jim was glad he made the request.\\



\enquote{If you don't mind my asking, if everything is a ten, why leave?} the man asked.\\



\enquote{I could go for a few sevens.}\\



\enquote{Fair enough.  Just go down that hall, and you're looking for the second door on the right.  Good luck.}\\



He found the room easily enough.  It was smaller than the main lobby, but with the same setup.  It was mostly white, and there was a man behind a desk and a single chair in front of it.  Jim blinked a few times.  It was the same man.\\



\enquote{Take a seat.}\\



\enquote{You're the same guy,} Jim said.\\



\enquote{I run things around here.  Go ahead, sit down.  Alright, so before we proceed I have to make sure you understand this all correctly.  For starters, once you find out the truth, you know that you can't go back?}\\



\enquote{I do.}\\



\enquote{And you know that you're leaving of your own free will, that you aren't compelled in any way to leave?}\\



\enquote{Well, I can only assume that, really.}\\



\enquote{Good enough.  And the last thing, you're aware that billions of souls are perfectly happy to be happy in spite of the paradox?}\\



\enquote{I am.}\\



\enquote{Great.  Now, as for the truth.  For the last 376 years, you have been living in paradise, and paradise is awesome.}\\



That's all he said.  He said it as if that was all that needed saying.  For the first time in a long time, Jim was angry.\\



\enquote{That's not enough,} he said through clenched teeth.  \\



\enquote{I'm afraid it never is.}  The man nodded.\\



\enquote{What about God?  The Devil?  Heaven and Hell and right versus wrong?  Who runs this place?  Where is it?}\\



\enquote{Oh.  Really?  That's not even part of the paradox.  God and the Devil are the same thing, and this where people go when they die.  That's all pretty much obvious.}\\



\enquote{But, but . . .}  Had he made a mistake coming here?  He suddenly wanted nothing more than to step back into the orgy's oblivion.  "But what about, I mean, who's \textit{right}
?"\\



The man spread his hands.  His face was brutally sincere.  \enquote{If you can't ask a meaningful question I can't help you,} he said.\\



Jim was speechless.  He had no idea what question to ask.  All those years, the chicken, the women, the booze, he always just figured the truth was sitting here on a silver platter, waiting for him.  God and the Devil are the same person?  What kind of truth was that?\\



\enquote{The exit is through that door,} the man said.\\



It was a plain door.\\



\enquote{What's on the other side?}\\



\enquote{I have no idea.}\\



\enquote{What??!  This is 1 Truth Road!  I'm giving up Paradise for this.  The fuck you don't know what's on the other end of a goddamn door!}\\



\enquote{I never went through it.}\\



\enquote{Then you don't know the truth!}\\



\enquote{I told you the truth.}\\



\enquote{What about the door?}\\



\enquote{That's where you leave.}\\



\enquote{What's behind it?}\\



\enquote{I don't have a clue.}\\



\enquote{Jesus Christ!}\\



\enquote{Not really.}\\



Jim went to the door and threw it open.  Before he went in, he looked back one last time.\\



\enquote{At least give me this.  What's the point of this place?  1 Truth Road.  It sure as hell ain't the truth.}\\



The man shrugged.  \enquote{It wouldn't be paradise with you moping around.}\\



Jim fell through the door.

More stories of Jim: \url{http://drowningdream.wordpress.com/jim/}