\chapter{Second Story}

Author: MrCadwallader

\enquote{God?} I managed to squeeze out between raggedy breaths. \\



I had never been very religious but in my delirium, that was my first thought. I remember the sky and the taste of blood before my eyes opened to pure brightness. I couldn't make out any detail but the light seemed to emanate from a winged, human-like figure. Were those horns or was it a halo? It all became blurry as tears welled up in my burning eyes. Even closed, I could see the figure seared blue-green into my eyelids.\\



Peals of thunder exploded in my brain, one after another like machine gun fire. It sounded vaguely like laughter. It wasn't a voice that responded but my body. It felt like invisible hands had gripped my ribs, my heart and stomach. Overwhelming nausea washed over me and I screamed as my body convulsed with pain.\\



\enquote{NO!}\\



All at once the pain stopped. It seemed I had answered my own question. I remained quiet, fearful that any further probing would result in more physical anguish. After some time a voice spoke out.\\



\enquote{You disappoint me. He was wrong about so many things. And yet right about others.}\\



I was terrified but eventually curiosity overcame the memory of pain. \\



\enquote{Who are you?} I asked timidly.\\



\enquote{He was the Creator but I gave you knowledge. I have been called deceiver and antagonist. I believe that these days you call me -}\\



\enquote{Lucifer,} it came out of my mouth as a whisper. \\



\enquote{Indeed.} The voice responded.\\



For a moment I thought I was in hell. There was nothing here except for brightness. I could feel the presence but the human-like figure had gone. Perhaps I had just imagined it. \\



I simply sat there for some time. It felt like centuries at the time but looking back now it was only a few moments before I became restless.\\



\enquote{What am I supposed to do?}\\



The voice responded for the last time, \enquote{Do as you will.}\\



So I did.\\



There was something special about this place in the early days. Everything was malleable. At first the silliest things please you. I've lived multiple lifetimes as James Bond, I became the world's greatest rockstar and a pro-athlete sometimes all at the same time. Of course, I've slept with literally millions of women. Men too. I've tried it all. From the sickest and most twisted, fastest and reckless to thousands of lazy, hazy Sundays. BBQs with family on sunny days to walking on the moon and slaying Ctulhu of the Deep. \\



None of that interests me anymore. I did not want to be the star anymore, so I became the director. I built my own universe from scratch. I created servants that would unflinchingly carry out my will and sing my praises eternally. I made a world and watched it grow but even that lost it's lustre.\\



In the end, there was only one thing left to do. I created my equal. And it was good. For the first time in a very long time I don't know what is going to happen. I see him ahead, my broken servants at his feet. And now he comes for me.\\


\asterism


Lucifer watched on. He had witnessed the same thing innumerable times before. They were all the same. Man and God fell prey to the same errors. Lucifer could not understand why the Lord had favoured them so. The tests would go on.\\
