\documentclass[a5paper]{scrartcl}
\usepackage{amssymb, amsmath} % needed for math
\usepackage[utf8]{inputenc} % this is needed for umlauts
\usepackage[USenglish]{babel} % this is needed for umlauts
\usepackage[T1]{fontenc}  % this is needed for correct output of umlauts in pdf
%\usepackage[margin=2.5cm]{geometry} %layout
\usepackage{hyperref}  % links im text
\usepackage{csquotes}
\usepackage{stackengine}
\usepackage{graphicx}
\usepackage{siunitx}
\def\asterism{\par\vspace{1em}{\centering\scalebox{1.5}{%\\
 \stackon[-0.5pt]{\bfseries*~*}{\bfseries*}}\par}\vspace{.5em}\par}

\usepackage{yfonts,color}
\usepackage{microtype}

\title{Welcome to Dell: The customer service call that fucked my life (Part 1)}
\author{SeriouZero}
\date{September 15, 2014}

\hypersetup{
 pdfauthor  = {SeriouZero},
 pdfkeywords = {Reddit, nosleep},
 pdftitle  = {Welcome to Dell: The customer service call that fucked my life (Part 1)}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\\
% Begin document                                                    %\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\\
\begin{document}
\maketitle

\yinipar{\color{black}I}'m not looking for help or advice, merely empathy; someone to understand and corroborate my experience. I need to know I haven't lost my mind. I'm a normal person, with a normal mind as far as I am aware. I've never been consistently scared of anything in my life, other than things like having my house robbed or missing a payment, normal fears anyone may have, until recently. \\


Please comment and let me know if you have ever experienced something like this.\\


I have an overnight job as a call teller at a large computer company. Its the same thing every night; even in the same order most of the time. Most nights, it goes as such: 7--9~p.m., calls from elderly people with simple problems that normally end in me explaining icons and opening the internet. (8--9 is usually the same people calling back to learn how to use the internet.) 9--10 - people trying to get free CD keys or complaining about software they have never purchased ( and drunk people who eventually got bored and hung up upon holding). Between 10~p.m.--7~a.m. is typically people from other countries or angry middle aged men who are insulted by the fact that they can't figure out how to install an update (somehow our fault even though most of these things are better referred to the company who handles the operating system). \\


Every day was nearly exactly the same. No one complained, although, no was truly happy at the end of the day. It was the kind of job that consists of \enquote{go, work, come home} and that was about the end of it every day; every two weeks I got a paycheck and that made it feel \enquote{worth it} in some sense or another\dots Most nights, I was the call center's supervisor from 7~p.m. to 7~a.m., I got relatively few calls and, since most of my underlings feared any potential reprimand from the higher ups, they would usually go to great lengths to help the customer and solve the issue, therefore eliminating half of the phone calls I would have received and reducing my calls to no less than customer satisfaction and a few calls that could not be solved by the customer service reps. \\


One night one of the operators forwarded a call to me. I picked up the phone, always instinctively reading the caller ID, it just said \enquote{call forwarding}. This wasn't too unusual so I picked up the phone and performed my usual spiel: \enquote{ Dell Computers, this is Lina, may I get your name and service tag number?}. The voice that responded was gruff and deep, almost unreal, and at first I thought it may even be a voice modulator, however our lines can detect this most of the time and nothing was unusual about the call according to our systems. \enquote{Why do you always chew your pens like that Lina?} responded the man. I paused, removing my pen from my mouth; I hadn't even realized I was chewing on it (a habit I've had since I could write.) \enquote{Excuse me sir, what issue can I assist you with today?} I responded slightly stumbling over my words, trying to process what he had said. \enquote{Lina, there are so many ways\dots} he responded in a strangely aggressive, deranged or maybe even seductive tone. \enquote{Um\dots OK sir, would you mind telling me what issues you are experiencing?} I said, growing more and more uneasy during the few seconds between our responses. \enquote{LINA} he in a very loud and crisp tone as though he were a school teacher calling me to attention, \enquote{Lina, Lina\dots fix your posture} he added. I immediately hung up the phone, adjusted from my slouched position and tried to process the conversation I had just had. As the day went on and more calls came through, I went about my normal routine with nothing else out of the ordinary. \\


I had nearly forgotten about the strange call until I left for the night. The moment I walked out of the building I felt uneasy. My floor was in the basement of the office complex and the ceiling was essentially even with the parking lot ground. I could see into my office by looking down through a small window level with my feet. The lights were off, but I felt so vulnerable standing outside in the open that I wished I was in that dark underground office. My car was parked about five minutes from the building in the parking garage. I walked quickly, shifting my gaze behind, left, right, forward and back again all the way to the car. There was no one in any direction. I made it to my car and nearly dove inside and locked the doors. I almost half expected someone to bang through the glass and wrench me out of the car. Instead, I turned the key, pulled out of the garage like a madman, and drew a heavy sigh as I exited the parking garage. I finally got back to my apartment, sat down on the sofa and starting watching TV. Around 9~a.m. I decided to hit the hay, I'll admit, sleeping in the daytime surely isn't the greatest perk of my jobs but I got thick curtains to cover the windows and it made it pretty easy to sleep. I brushed my teeth before bed, noticing some of the bristles were missing. I shrugged it off, I must bite that the way I bite my pens without even realizing. I thought of the mysterious caller from earlier that night but instantly put the thought out of my mind.\\


Just as I was drifting off, I felt my phone vibrate from beside me in the bed. \enquote{Who the fuck?} I muttered sleepily and answered the phone. \enquote{Hello?} I said groggy and unwilling to open my eyes. \enquote{Lina\dots dear} the voice said under some feedback and static. \enquote{Who is this} I mumbled starting to rouse myself. \enquote{Lina, you shouldn't sleep on your side, that's why you slouch so much}. I nearly dropped the phone and immediately sat up. He continued \enquote{Lina, you're going to need that spine, you know}. \enquote{WHO THE FUCK IS THIS?!} I screamed. Before the man could respond, I removed the battery from the phone and threw it across the room. I pulled back the curtains one by one slowly to check if someone was outside. No one was there. I contemplated calling 911 but I wasn't sure what I'd say. I'd been in psychiatric care in the past and most of my family disowned me for it. I was afraid the police would only come to the conclusion that I was having another 'episode' and my family would only further distance themselves and I'd be stuck in a hospital. I finally worked up the courage to leave my bedroom after checking the closet, investigating all the windows three or four times and even lifting the mattress. I walked around checking the entire apartment. All the locks were still secure on the doors and windows and I began to calm down. \\


It was probably just a young family member playing a sadistic joke about my previous mental issues I figured, beginning to calm myself down. I decided to make a cup of tea and try to get some more sleep. I poured a fresh cup of tea and stretched my arms while yawning almost triumphantly, having felt like a detective who just solved a great case. I walked through the living room towards my bedroom when something caught my eye. On my coffee table sat a red envelope. \enquote{What the\dots} I mumbled to myself, striding over and grabbing the envelope. Nothing was written on the outside, I opened the envelope and inside was a blank white card. As I opened the card something fell out onto the floor, I bent down, holding my stiff back , and watched several toothbrush bristles beginning to sink into the carpet. Inside the card was written \enquote{Bend with your legs, not your back Lina}


\clearpage
\section*{Stories of this series}

\begin{itemize}
    \item Story~1: Part 1
    \item Story~1: Part 2
\end{itemize}
\end{document}