\documentclass[a5paper]{scrartcl}
\usepackage{amssymb, amsmath} % needed for math
\usepackage[utf8]{inputenc} % this is needed for umlauts
\usepackage[USenglish]{babel} % this is needed for umlauts
\usepackage[T1]{fontenc}  % this is needed for correct output of umlauts in pdf
%\usepackage[margin=2.5cm]{geometry} %layout
\usepackage{hyperref}  % links im text
\usepackage{csquotes}
\usepackage{stackengine}
\usepackage{graphicx}
\usepackage{siunitx}
\def\asterism{\par\vspace{1em}{\centering\scalebox{1.5}{%\\
 \stackon[-0.5pt]{\bfseries*~*}{\bfseries*}}\par}\vspace{.5em}\par}

\usepackage{yfonts,color}
\usepackage{mystyle}
\usepackage{microtype}

\title{Death at 423 Stockholm Street}
\author{C. K. Walker}
\date{April 11, 2014}

\hypersetup{
 pdfauthor   = {C. K. Walker},
 pdfkeywords = {Reddit, nosleep},
 pdftitle    = {Death at 423 Stockholm Street}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\\
% Begin document                                                    %\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\\
\begin{document}
\maketitle

\begin{shadequote}[l]{Onegin}
OH GOD I USED TO LITERALLY LIVE AT 234 STOCKHOLM STREET NO BUENO NO BUENO
\end{shadequote}

\begin{shadequote}[l]{extrasmallbunch}
Well, that's not at all what I was expecting.
\end{shadequote}

\begin{shadequote}[l]{LastStark}
Holy shit.
\end{shadequote}
\clearpage

\clearpage

This story was written by C.~K.~Walker and first published on Reddit under the
pseudonym \textit{The\_Dalek\_Emperor}. Then
Martin Thoma typesetted it professionally.\\

The work is licensed under the CC-BY 4 license.\\

This PDF and more as well as the source files are available at
\url{github.com/MartinThoma/free-books}.\\

If you want to contribute a store, images for an existing story or report
errors you can contact Martin Thoma (info@martin-thoma.de).

\clearpage

\yinipar{\color{black}W}e've always lived at 423~Stockholm Street, so there really wasn't ever a time that I didn't hear the creature. He'd been living in the room on the other side of my wall since I was born.\\


When I was a very young child, I thought He was my friend. I would knock and He would bang back. I would giggle and He would mumble words to me that I couldn't understand. I thought He was there to protect me from my nightmares. But as I got older, I started to be afraid. My parents insisted that there wasn't a room on the other side of my wall. Over time, I realized that He wasn't my friend at all. That's when the scratching, moaning and sporadic banging began to scare me.\\


When I was eight I finally broke down and told my parents about the creature in my wall. I was terrified that He would come into my room one night and kill me. My mother rolled her eyes and told me it was mice. She never listened to me, anyway. My father agreed with her that it was animals, but he hugged me and told me he would protect me and not to be scared.\\


So from then on whenever I'd hear the noises I would scream for my father and he would come running into my room less than a minute later to see what the matter was. I would point at the wall and cower. My dad would smile, bang on the wall with his fist and say: \enquote{Quiet down in there or else!} The noise would stop, I'd give my dad a teary smile and he would hug me. He was always my protector. I miss him so much, now.\\


As I matured into a teenager I started inviting my friends to sleepover. They didn't believe my stories at first but after one night in my room --- they were convinced. We called ourselves the Stockholm Street Ghostbusters and we spent hours trying to exorcise the entity (a demon, according to our research) through awkward séances and Ouija boards. We decided that the scratching must be the creature etching satanic sigils and drawings into the other side of my wall.\\


One slumber party, running on heightened bravado and caffeine, I waited until the familiar scratching started and I pounded on the wall, just like my dad. \\


\enquote{QUIET DOWN IN THERE OR ELSE. YOU'RE ALREADY DEAD. THE LIVING ARE TRYING TO SLEEP!} \\


We giggled and my friends were impressed --- for a moment. I should have known not to provoke him. \\


Suddenly there was an answering enraged banging on my wall, louder than I'd ever heard, and a sort of angry yelling. We all screamed and hid in the closet, yelling for my dad. When he came running, my friends begged him to take them home. I was left alone while they were gone. I could feel Him, almost see Him impatiently pacing behind the wall, back and forth, 5~inches of wood and wallpaper between He and I. I was so scared that I stayed hidden in the closet. Then the scratching started again.\\


That was when I realized what it was doing: it was trying to carve its way through the wall and into my bedroom. I whimpered at the thought and then scratching stopped and the banging resumed on the walls. It didn't stop again until the headlights of my dad's car lit up my room. I cried until my dad, always the hero, came sprinting into my room and banged on the wall. \\


\enquote{It's still in the walls, Dad!} I wailed.\\


He nodded, gave me a pitying look and pounded his fist on the demon's wall. \enquote{Quiet down in there or else!} \\


Then he held me, let me cry out my fears, and told me it was okay if I slept on the sofa that night. Sometimes I thought he believed it was all in my head. But it wasn't. The murmurs, the knocking, and the scratching, I'd been hearing it all my life. It was real. But if he didn't believe he never let on and never made me feel crazy. He just played along. I guess I never really understood my dad. \\


One night when I was~16, I was awoken by an otherworldly, ear-splitting scream. It was so loud, so high and so piercing that I screamed as well, in terror. The scream ended abruptly then and a moment later my dad came running in.\\


\enquote{You heard it!} I cried as my body wracked with sobs. \enquote{How could you not hear it? You had to have heard it.}\\


\enquote{Oh sweetie.} My dad sat at the end of my bed, his hair disheveled and a far-off look in his middle-of-the-night, bloodshot eyes. \enquote{Of course I heard it, but it was just an owl, I'm sure of it. We've been seeing a few in the neighborhood.}\\


\enquote{No dad, listen to the walls.} 
\enquote{Lindsey---}\\


\enquote{Please, Dad.}\\


He sighed but nodded and we sat and listened for awhile. I needed my dad to know the truth and to finally believe me. We were all in danger.
But no more sounds came from the wall that night.\\


I didn't hear Him again after that, not for a long time. The wall suddenly felt empty to me for the first time in my life. Maybe it was dormant or maybe it had been called back to Hell. But either way, I knew it would be back.\\


Oddly, when the creature did return I didn't really notice at first. After 16~years it was simply white noise to me: a background soundtrack as familiar to me as my own face. It took so long for me to process that it was back that I can't put my finger on when it actually started. I think that's what sealed our fates, in the end. The noises were just so inherent to me that I failed to understand how unusual they really were, and had been all along. When I finally did realize what I was hearing I'm ashamed to say I felt almost relieved. \\


The haunt progressed in the same cycle it had all my life. First, the groans, then the banging, then light, lazy tapping, and then, finally, the scratching, always the scratching.     \\


I'd told my dad about the scratching, and about how I thought the creature was trying to rip through the wall and into my room. My dad laughed and told me there were 3~inches of solid metal on the other side of my wall and that nothing; not mice, raccoons, feral cats or even ghosts could come through my wall. And he should know, he'd built the house himself. And besides, he assured me, he would always be there to protect me. But in the end, he wasn't.\\


Since I was moving out in a year, I decided I had no choice but to just stick it out. After 16~years with Him, what was 12~more months? I grew unconcerned, lazy, and complacent. I ignored the noises, even started to bang back, again. I used logic to pacify my fear: whatever it was, it couldn't come through the wall. If it could, it would've done so years ago. And I sensed that more than anything else in the world, it wanted OUT. And since it was still in there, obviously, it was trapped. And I was right.\\


The night the door was opened is the most vivid memory I have. I was at a friend's house when my mother called me and told me to come home immediately. This, in itself, was strange as my mother barely even acknowledged me and never, ever called me.\\


I drove the 5~miles back to my neighborhood but I had a hard time getting in. I started to panic as I desperately weaved through all the media vans, police cars, and SWAT trucks. I had to park and walk the final three blocks to my house, tears rolling down my cheeks as I realized that my street was at the epicenter of it all. Because I knew. As soon as I saw my house, I realized it --- my dad must be dead. It had finally gotten out and it had killed my dad.\\


I took off at a dead run then, ignoring all the voices yelling at me to stop. I dodged in between the vehicles, pushing past dozens of people, ran through the crime scene tape and directly into my house --- and there it was. Across from the living room, next to my bedroom, the hall closet stood with its door open. All the jackets and sweaters had been pulled out of it and on the back wall I saw it --- another door.
For whatever reason, no one stopped me. I stumbled into the closet, through the hidden door, and out into the room I'd always known was there. But it wasn't what I thought it'd be.\\


The media called my dad The Skinner of Stockholm Street. And from what I saw in that room, it was a very fitting name. There were knives, all sorts really. And there were metal devices stacked along one wall, at least a hundred of them. Most I didn't recognize, but a few I had seen in history books. There were 4 set of manacles, a wall of chains and rolls of duct tape. In the middle of the room there was a flat table which was, very clearly, blood soaked. A tall stool sat at the head of the table.\\


But the worst of it was the wall --- my wall. Every inch of it was covered in carvings. But the carvings weren't satanic or evil like I'd thought. 
The carvings were words.\\


\textit{Jacob, I love you. Diana Hobb}
\\


T\textit{ell my father I forgive him. Brian Woodlin}
\\


\textit{Tara, I'm so sorry. Michael Mcnulty}
\\


\textit{Tell my daughters they were my world. Angela Waterstone}
\\


According to the evidence file there were over 60 of these messages. And I made myself read every single one. They haunt me every night. I had spent ten years tormenting them and they would now forever torment me.\\


I live in a hospital now and I can still hear the scratching. Every time I close my eyes, I hear it. I haven't really slept in a year. My doctor says if I don't sleep soon, I'll die. I spend my days watching news coverage of my father's trial, and I spend my nights staring at the walls. The drugs don't work, but they keep giving them to me anyway. And though I try every night, I can never fall asleep. I always hear the scratching. And I always will.
\end{document}