\documentclass[a5paper]{scrartcl}
\usepackage{amssymb, amsmath} % needed for math
\usepackage[utf8]{inputenc} % this is needed for umlauts
\usepackage[USenglish]{babel} % this is needed for umlauts
\usepackage[T1]{fontenc}  % this is needed for correct output of umlauts in pdf
%\usepackage[margin=2.5cm]{geometry} %layout
\usepackage{hyperref}  % links im text
\usepackage{csquotes}
\usepackage{stackengine}
\usepackage{graphicx}
\def\asterism{\par\vspace{1em}{\centering\scalebox{1.5}{%\\
 \stackon[-0.5pt]{\bfseries*~*}{\bfseries*}}\par}\vspace{.5em}\par}

\usepackage{yfonts,color}
\usepackage{microtype}

\title{Death of Deepwood, Pennsylvania}
\author{The\_Dalek\_Emperor}
\date{July 01, 2014}

\hypersetup{
 pdfauthor  = {The\_Dalek\_Emperor},
 pdfkeywords = {Reddit, nosleep},
 pdftitle  = {Death of Deepwood, Pennsylvania}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\\
% Begin document                                                    %\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\\
\begin{document}
\maketitle

\yinipar{\color{black}I} padded quietly through the dimly lit gift shop, pulling the straps of my backpack tighter over my shoulders like a security blanket. When I reached the opposite door, I leaned my head against it and tried to calm my rapidly beating heart. \\


Taking several deep breaths, I slid Scotts's keycard through the blinking card reader and was rewarded with a green flash and another soft click. The creature was right where I'd left it, as still as the statue it was pretending to be. \\


I took my time wandering around the room, my eyes never leaving Jameson Scott's prize exhibit. If the demon was as satisfied and successfully warded as Scott bragged it was, than the creature either wouldn't notice or wouldn't care about my presence.  I was starting to hope he was right. \\


When I finally came around to face the statue, I approached it slowly and unbuckled the velvet rope with a shaky hand. I was so close to it now that all I could see when I looked up was the underside of its gigantic head. I suddenly wondered if years of schooling would help me read the words inscribed on the statue's stone platform. I bent down and started to pull up the velvet covering when I heard a quiet scrape above me, like stone on stone. It was a sound I'd heard before, in the soundtrack of my nightmares.\\


So I had been right all along, the statue wasn't dormant. It was a hollow victory. I dropped the velvet and backed away from the statue, trying to determine what had moved. Nothing had changed to my naked eye, but I know what I heard.\\


Bumping against the back wall, I decided to play a wild card. I needed it to move perceptibly if I wanted proof that the thing was still dangerous. I turned away from the demon and faced the wall, using an arm to brace myself. I couldn't believe I was doing this.\\


I pushed my chips all in. \\


\enquote{Do you really think I'm scared of you, after all these years?} I asked quietly, my voice echoing around the room like a gunshot. \enquote{You're just a piece of rock now. Harmless to me.} \\


I held my breath and waited. Nothing.\\


Feeling both disappointed and relieved, I sighed and turned around, dropping the keycard as well as my jaw. Though it hadn't made a sound, the statue was now not only facing me, but leaning out, as far off its stone platform as it could. Its mouth was open and, almost imperceptibly, growing wider by the second. \\


\enquote{You can't leave your platform.} I breathed, as much to myself as the creature. My whole body was shaking and I was quietly backing up, slowly, slowly to the door. I'd gotten what I'd come for, now it was time to leave.\\


It happened in the breath of a second. There was a sudden crack as the demon's tail whipped through the air behind it from one side to the other, as though it were not made of stone but of flesh and blood. The glass encasing it on either side shattered, the makeshift wall behind split in two and the velvet ropes came crashing down; one of the poles sent a sigil flying across the room. \\


I screamed like I'd never screamed before as the creatures neck seemed to stretch across the room toward me, one of its wards no longer effective. I turned my back on it and ran for the door realizing too late that the keycard now lay under a heap of rubble. I reached the double doors and tried to jerk them open, hoping they weren't locked from the other side. They were.  The creature was once again still as stone, everything but its eyes, which followed my every move, hungrily.
I beat on the door, yelling for security and wondering if I was doomed and which thought would be my last. In my hysterical panic I suddenly remembered how I had escaped this fate 13 years before. I stumbled back from the doors as much as I dared and ran at them, shoulder first.\\


They moved, creaked even, but ultimately laughed at my efforts. These were no rotten, decaying church doors. Crazed with fear I backed up to try again and this time just as my shoulder reached the door, it opened from the other side and I went spilling over on top of something hard -- or someone. \\


He rolled over and I passively registered that I'd landed on an enraged Bannock. He was standing and pulling me up by the strap of my backpack before the door had even closed behind us.  \\


Bannock struggled to say something, trying several times, but was too angry for words. I didn't care; I threw my arms around him just happy to be on the other side of the door. \\


He didn't hug me back, just froze stiff and waited for me to get off of him. When I finally pulled back, I pulled my hood down and looked him full in the face. He wore a decidedly guarded look.   \\


\enquote{Did you see what it did?} I asked, pushing hair back from my face, \enquote{That thing is not dormant at all. Tell your boss that, and that it needs to be moved. Tonight, if possible.}\\


In lieu of a response, Bannock grabbed my arm and headed toward the lobby. Since it was away from the exhibit room, I didn't care; he could take me to jail if he wanted, as long as Jameson Scott heard what happened here. I'd made my point to him and lived to tell the tale. \\


Or had I? I suddenly wondered.  Honestly if I'd learned anything in that room, it had been that the creature hadn't forgotten me- the girl that got away. My life was a black mark on its record, an insult.  And I had gone into its lair and challenged. What did I \textit{think}
 was going to happen?\\


Of one thing I was abruptly certain: it wouldn't stop until it had my life. The creature would burn through a hundred cities, perhaps a thousand, to claim me. It had told me all of this somehow, hadn't it?\\


I suddenly realized my mistake. The creature had been dormant when I'd arrived in Lannenburg as it'd been dormant 13 years before in Deepwood. And once again I had awoken it from a harmless slumber. How many would pay the price this time?   How many people had to die before the end? \\


Finally understanding the true cost of my arrogance, I let out a muffled cry and faltered, wondering with revulsion if perhaps I should just go back and face my fate. \\


\enquote{Wait.} I coughed, trying to ply the guard's fingers from my arm.\\


Bannock suddenly spun me around and pinned me against a wall, his arms braced on either side of my head. My eyes snapped up at him in shock and I recoiled from what I saw there.\\


\enquote{What the fuck are you doing here?}\\


\enquote{I was, I was just-}\\


\enquote{Why did you come back, Katie? After all these fucking years?}\\


My objection died in my throat. But it couldn't be. It wasn't possible. And yet\dots somehow it was.\\


My legs gave out under me, but Jamie caught me on the way down. He was older than he should have been, and stronger than I'd ever thought the skinny kid from Middlesbrough could be. But his eyes hadn't changed, and it was Jamie all the same. Even his expressions were familiar to me, I realized. What I'd first thought was seething anger was actually just barely controlled fear. Had the creature killed me after all? Was I swirling in the dark abyss with Jamie and all the others who had been taken?\\


\enquote{Jamie?} My voice broke over his name.\\


\enquote{Christ, Katie, you need to leave now and never come back. Hell, leave the country if you can. He'll never stop looking for you now.}\\


I couldn't register what he was saying. Who wouldn't? Leave what country? Jamie\dots how was Jamie here? He kept me pinned there; his hold rigid, his eyes desperate and little bit pissed off.\\


\enquote{Jamie,} I tried again, \enquote{how did you\dots }\\


\enquote{How did I know you'd come here? When has the word 'no' ever kept you from something you wanted?}\\


\enquote{No, I mean how-}\\


\enquote{We'll take her from here, Bannock. } A voice behind him interrupted me. \\


Jamie slowly turned to face the three men, only one of which I recognized.\\


\enquote{This one has been too much trouble. I want her gone.} Jamie returned with ice in his voice.\\


\enquote{Mr. Scott says we're not to take orders from you anymore, Bannock. Give her here.}\\


Jamie suddenly pushed me out of the way and I went sliding across the floor, the wind knocked out of me.  A rushing filled my ears as I tried desperately to catch my breath. When my hearing came back, Jamie was yelling at me.\\


\enquote{Go!}\\


I looked back to see two men down and Jamie struggling with the third. My sneakers struggled for purchase on the slick marble floor and when they finally found it, I was up and running toward the lobby on the wings of adrenaline. I suddenly heard a sound like a book slamming onto a table. \\


I spun around just as Jamie went down, clutching his shoulder. He fell on top of the man he'd been struggling with -- who was now unconscious.   Blood began to drip over his fingers and I went sliding across the floor as I tried to stop to double back for him. \\


Jamie started to say something but passed out mid sentence. His hand dropped from his shoulder and thin tendrils of blood began to race each other down his chest.\\


\enquote{Well, now that is impressive,} Jameson Scott stepped forward from where he'd been leaning against the door. \enquote{And I'm not impressed by much at my age.}\\


I stumbled over to Jamie, but Scott stopped me with a single click of his gun. He walked over and rested a foot on Jamie's chest. I froze where I was. \\


\enquote{I saw you take my keycard, you know. You played the role perfectly. In fact, \textit{everything}
 went according to plan. Except him.} Scott kicked Jamie in the ribs but he didn't make a sound.\\


\enquote{What do you want?} I spat.\\


\enquote{Your name came up. I want you to die.}\\


\enquote{Why?}\\


Scott gave a pretentious scoff. \enquote{This isn't a James Bond movie, Miss Ross, I don't need to explain myself to you.}\\


\enquote{But you will, won't you? You want me to know how clever you are.} I was playing with fire but why not? We were far beyond caution now. \\


\enquote{Hmm, you're quite bright. There might have been a place for you on my staff\dots if things had been different.}\\


\enquote{Don't flatter yourself. Why then? Why are you giving a demon what it wants? Didn't it kill someone you loved?}\\


\enquote{My daughter, actually. And why? It's my gift to a world I was born too late into. You know, I was fifty by the time the internet was invented - fifty! What sad irony then, that I was a technological genius. Oh but the universe does love its sick jokes. Do you realize I've single-handedly guided the history of modern technology? It's true. But I reached my seventies and then my eighties, and my vision began to fail, my hands would shake, I'd forget coding. I could barely manage to read at one point.}\\


\enquote{I'd made millions, but I hadn't even started. I decided the world couldn't afford to lose me yet. So, I tracked down every piece of ancient lore I could that may help me reclaim my youth. Most of it was rubbish, of course, but I was desperate. I'd almost given up -- until Metaraxes found me.}\\


\enquote{I knew what he was as soon as I saw him. So I bought him and warded him using the sigils I'd read about in ancient text.  Of course, there was an expensive trial and error period; many of my staff were killed in the process. But eventually, we discovered the right sigils. The first thing I did was track down the man whose name was etched into the granite at Metaraxes's feet. I presented him for sacrifice and I was rewarded.}\\


\enquote{That was six years ago. I adopted a new name and started a new company. All was going well until your name came up about four years ago. It really stumped me because Metaraxes only desires those who are connected to him, somehow. I didn't know who you were and you're far from the only Caitlin Ross in the world. I did \textit{try}
 several others. Metaraxes would take them, for certain, but the name never changed. I was getting desperate.}\\


\enquote{So you can imagine how happy I am that you showed up on my doorstep.  God is telling me that he approves of my methods and that I must stay alive for the good of humanity. My company is in the middle of revolutionizing surgical robotics, for Christ's sake! I will take a few lives to save a million.}\\


Furious at his arrogance, I struggled to keep my voice level. \enquote{Don't lie to yourself, Scott, you're no hero, just an old man afraid to die.}\\


\enquote{No, Caitlin, I'm just a man refusing to grow old. What can I say? I'm determined and resilient.  I want to be young until the day I die.}\\


\enquote{That's not resilience, that's vanity. Vanity is what you're buying with my life.} \\


\enquote{There's always a price for social change, Miss Ross. And today, the cost is you. Oh, but you look upset. Don't be afraid of death, my dear, not for such a worthy cause.}\\


\enquote{I'm not afraid of death and I don't care about your diabolical plan, I just want you to get to the goddamn point.} Jamie's breathing was growing shallow and my voice dripped with animosity.\\


\enquote{As you wish.} Scott nodded at something behind me and then there was darkness.\\


When I woke, I was lying on a cold marble floor, my brown mess of hair fanned out underneath me, stiff with dried blood and my wrists bound. I sat up slowly and tried to brush the hair out of my eyes. I knew where I was, there was no point in turning around to see it, but I did anyway.\\


It wasn't the fact that my name was engraved at the base of the statue that the velvet cloth had covered. It wasn't the wards, which had been moved from the demon's feet to the doors and walls of the room. It wasn't even the fact that the demon's head was turned as to be looking directly down at me.\\


No, what terrified me most in that room was the man leaning against the wall, hands bound behind his back, as condemned to death as I was.\\


The blood on his chest had dried and he was awake; his eyes only partly open, watching me with an unreadable expression.\\


\enquote{You look like shit, Jamie.} I said matter-of-factly as I pulled myself up to lean against the base of the statue, the only thing nearby.\\


\enquote{I've been busy,} He said, his mouth curling up into a sarcastic smile.\\


\enquote{I'm sorry I killed you. Again.} I tried to smile back, if only to keep the tears at bay.\\


\enquote{Nah, we'll survive this.}\\


\enquote{I admire your optimism, but look around.} I rested my elbows on my knees and sunk my head into my arms.\\


\enquote{I lived through it once before didn't I?}\\


\enquote{Yeah about that - how?}\\


\enquote{About a week after you left things started disappearing around town: people, buildings, even roads. No one remembered them but me. Then one day, I woke up in an empty house. My dad and my brother were gone. So, I fled to the only place I knew was safe.}\\


\enquote{The Damned Church.}\\


Jamie shrugged. \enquote{I figured it was the one place the demon would never go. I don't know how long I lived there, but it felt like years. I slept at the church and traveled to nearby towns to steal what I needed to live. And then, one day, the towns were gone. All of them.}\\


As he spoke, I watched him, memorizing every detail of his face. Even when I was nothing, I hoped something was left of me, a little piece that would remember him.\\


\enquote{So, I decided to find the thing. My dad was gone; my mom didn't remember me, and the only person who knew who I was lived a thousand miles away. So I went from town to town until I found it. It was just there; standing in the center of town. Nobody even thought it was weird.}\\


\enquote{I was a pro at drawing sigils by then since I'd spent some much time at Deepwood, and sigils have to be perfect to work, so I tried to ward it. It would take a little while, but the statue always managed to break them. I'd find it a little further from its base every night. People didn't even seem to notice the statue had moved, what they did notice, however, was some kid loitering around their town.  Since I looked older, and the town was getting wary of me anyway, I joined the local police force and spent my nights on patrol downtown, keeping an eye on the thing, reapplying sigils. Occasionally, I would wake up outside and I'd know my wards had finally failed. Then I'd have to track it to a new town and start all over.}\\


\enquote{Why didn't it just kill you?}\\


\enquote{I asked myself that until a few years ago when your name came up. I think it needed me - to find you. Ironically, in the end it didn't need me at all. You came anyway.}\\


I thought about that and wondered for the first time if I actually \textit{had}
 come back to prove myself sane. Had I really intended to kill it? Or prove I'd been right? Or had it actually been about Jamie all along?\\


\enquote{It took a long time, and a lot of towns,} he continued, \enquote{but I finally figured out what I was doing wrong. A sigil will slow it down, but in order to stop it the ward needs to be blessed. And not just by anyone - by the second son of a Roman catholic, preferably from Assisi, Italy, or at least near the region. Don't ask me how I figured that out.}\\


\enquote{So what happened to your second son from Assisi, Italy?}\\


\enquote{He disappeared.}\\


\enquote{Shit.} I pushed my hair back again with my bound wrists.\\


\enquote{Yeah. By that point I was a sheriff and I'd been a city over. I came back to town to find my exit missing. The statue was gone. And that's when Jameson Scott got a hold of it.}\\


\enquote{And that's why were you protecting him?}\\


\enquote{You think I was protecting \textit{him}
? No, he was transparent about his intentions from the start. I applied to be on his detail but was denied - no name, no experience. I only got on because I was able to take out all of his bodyguards in a sort of hand to hand combat trial. Guess all those trips through the police academy finally paid off.}\\


\enquote{Agreed. How does Jameson Scott know more about that statue than we do?}\\


\enquote{ Because he had almost 80 people on his staff who did nothing but travel every corner of the globe looking for any scrap of information on 'Metaraxes'.  We aren't the first ones to live to tell the tale. Just the first to stick around.  I did all I could to keep people away from that thing. A name would be engraved on it one day, and a new name the next. It took me a long time to figure out what he was doing. And by then\dots your name had come up. He's became obsessed with you and I damned sure wasn't going to let him find you.}\\


\enquote{Well that explains why you were mad when you saw me.}\\


\enquote{Mad? Katie, I've never been more terrified in my life. I spent years leading him down false paths only to have you present yourself like a lamb for slaughter.}\\


\enquote{I'm sorry, Jamie. I wasted all your fucking time.  You spent 13 years trying to protect me and I spent all that time trying to forget you.} \\


\enquote{Well, it's no less than I wanted for you. To forget about this place, and me.}\\


I heard the familiar stone on stone sound from above me. \\


\enquote{Is there any chance of reasoning with him? Your boss, I mean?}\\


\enquote{Not likely,} his voice was dark. \enquote{He fed his own daughter to that thing.}\\


\enquote{He what?!}\\


\enquote{For the greater good, he said.}\\


\enquote{God, Jamie, I don't want to die. I don't want \textit{you} to die.}\\


\enquote{You're not going to die here, not today.}\\


I ignored his optimism. \enquote{Why do you think it hasn't killed us yet?}\\


Jamie sighed. \enquote{It's trying. Scott kept a close watch over his demon but I managed to get one thing by him. That statue is sitting on a sigil the size of a mini cooper. It's not blessed - but it's big.}\\


\enquote{You're a brilliant bastard, James Karras.}\\


\enquote{Well, I've sure had a lot of time.} I heard a clicking sound and Jamie stood up, tossing a now worthless pair of handcuffs on the floor.\\


He walked over and stood me up; using whatever tool he had picked his own cuffs with to free me. I heard them click but when they fell to the floor all I heard with the loud grinding of stone on stone again. It was louder and longer this time.\\


\enquote{Don't look at it, Katie. Don't look up.}\\


\enquote{Jamie\dots } I breathed, terrified. Suddenly, a face appeared behind Jamie. But this time, I wasn't hypnotized by it. Jamie saw the color drain from my face and grabbed me.\\


\enquote{Follow me- now!} He yelled, pushed me in front of him to the giftshop door. I heard more movement from behind us and turned around while Jamie typed a long sequence of numbers into the card reader keypad. The creature had turned its head and it was watching me. It was alive, as alive as it had ever been. The statue took a step off its platform which shook the museum floor. Its movements were silent, yet fluid and flexible, like a cartoon on mute.\\


\enquote{Jamie\dots }\\


\enquote{Working on it!} Suddenly the key pad flashed green and the door clicked open. Jamie drew a black marker out of his pocket and drew a long line down the middle of the sigil, negating it. \\


\enquote{What are you doing?!}\\


\enquote{Just trust me.} Jamie pushed me out the door.\\


We slammed it behind us and tore across the giftshop to the exit. The door was locked. I turned around to tell Jamie as much but he was already hurling a table through the window. It shattered just as I saw the door on the other side of the room begin to bend as it was pushed in from the other side.\\


\enquote{How did you unlock that door?} I asked as we ran across the parking lot.\\


\enquote{Scott isn't the only one who's good with programming.} Jamie yelled back. \\


I followed him to a black jeep sitting at the edge of the parking lot. We jumped in just as a loud bang echoed across the asphalt, god only knew what it meant. Jamie shoved his keys in the ignition and turned the car over. The beginning chords to \enquote{Highway to Hell} blasted from the speakers.\\


\enquote{Why not?} I shrugged as I turned it up. Jamie nodded and peeled out of the parking lot. We tore through town like the devil himself was chasing us - which wasn't far from the truth.\\


It was early, the first rays of sunlight streaming through the trees as we hit the highway. We hadn't gone more than 5 miles when a white SUV appeared behind us. It followed at a considerable distance.\\


\enquote{Why aren't they overtaking us?}\\


\enquote{Because this is what he wants. Scott knows where we're going.}\\


\enquote{Where \textit{are} we going?}\\


\enquote{Deepwood.}\\


\enquote{Fuck.} I said as I leaned back in the chair. But I trusted Jamie, so I didn't object.  \enquote{Won't it take the creature days to make it there?} I asked, eyeing Jamie's speedometer, which was at 90. \\


\enquote{It doesn't always move like that. It sometimes travels on another plane. I can't explain it. Everything changes and warps around that thing, even time. That's why I'm about 8 years older than I should be.}\\


He suddenly whipped off the road and headed for the treeline. The truck behind us did the same and we maneuvered randomly through the trees, though I figured Jamie knew where we were going. I held on for dear life and watched him expertly navigate the almost hostile terrain or downed trees and deep ditches. \\


\enquote{How far?} I asked after ten minutes.\\


\enquote{6 miles but you know how time is out here.} \\


Did I ever. Four minutes yet somehow six miles later we bumped over a set of railroad tracks and arrived at the Damned Church, which looked smaller and more impotent than it did in my nightmares. The front door opened easily this time and I gave an involuntary shudder when I saw the Jesus statue - looking more judgmental now than ever before. The trapdoor was open.\\


\enquote{You lived here for years and you never closed the trap door?} \\


\enquote{Believe me, I tried.} Jamie grabbed my hand and guided me to the hole in the floor. \enquote{We have to go down there.}\\


\enquote{Fuck no.} I snatched my hand away.\\


\enquote{It's the only way this will end, Katie.}\\


\enquote{You've got to be kidding me,} I muttered as I took the first reluctant step down.\\


\enquote{Wait,} I suddenly stopped. \enquote{You said it wouldn't ever come back here.}\\


\enquote{It would for you.} \\


Jamie followed behind me and took the stairs down, on shaky step at a time. Jamie followed behind me, flashlight in hand. I didn't see it until right before we reached the bottom. The demon was already here waiting for us. It stood in the same position we'd first found him in 13 years before, though this time it's face was not stone. The demon's eyes swept across the room in a wide arc, his tail was wrapped around the bottom of the staircase.\\


\enquote{If he was already down here, why couldn't we stay up there?} I whispered.\\


\enquote{He wasn't.}\\


There were no wards to protect us now, and no where to run. I couldn't help thinking this was a bad plan.\\


\enquote{Well, he's here now, so let's go.}\\


\enquote{We can't Katie. If we leave now, he will too.}\\


\enquote{Well then what's your plan, Jamie?}\\


Jamie said nothing, just stared at the demon, who was now staring back at him. Suddenly I felt something like a tug, in the pit of my stomach. I stepped back, and then it happened again. I looked up into the creature's eyes, which had moved to mine and suddenly realized what was happening. There was another tug, harder this time, and I felt my mind, if not my body, being pulled toward the demon's head. A long black tongue jutted out to welcome me and the creature's mouth began to widen. So this was it. The nothingness.\\


The demon's mouth was so wide I could have simply walked into it, if I had a body. The blackness started to close in on all sides, creating a sort of tunnel vision and then, in a violent jolt, I was snapped back into my body, a perfect sigil drawn on my chest in black marker. The creature screamed, an earsplitting sound, and Jamie flung me over his shoulder before I had even reestablished my bearings. We were to the top of the staircase in under a minute, the demon still emitting a deafening wail. \\


\enquote{I'm sorry!} He yelled \enquote{I was sure it would come for me first!}\\


We burst into the nave, and Jamie, seeing our company before I did, pushed me across the alter toward the crucifixion, which I took out as I fell. I scrambled back, kicking it away from me as I did. By the time I looked up, Jameson Scott was standing in front of the trapdoor, a gun to Jamie's head. His men hung back, but looked eager to get involved at a word from their boss. \\


\enquote{Get back down there, Miss Ross.} \\


\enquote{Fuck you.} My last word was drowned out by a loud cracking sound that echoed  through the little church as the spiral staircase came crashing down below. \\


\enquote{Katie, don't-} Jamie caught a knee to the ribs, some of which I was pretty sure were already broken. I scrambled back further. \\


\enquote{There's- there's no staircase now. There's no way to get down there.}\\


\enquote{Oh, sure there is.} Scott sneered. His hired men laughed. \enquote{You're going to die either way. At least \textit{this}
 way, you'll save his life. Metaraxes is trapped down there for the time being, so it's to the cellar you must go. Perhaps you shouldn't have injured him by breaking his bond \textit{mid-feed}}\\


\enquote{Katie,} Jamie growled. \enquote{Don't be fucking stupid. Just run.}\\


\enquote{Fuck no, Jamie. I didn't leave you in this place then and I wont now.} It was time to pay my dues. I stood up to walk to the edge of the trapdoor. Perhaps, if fate was kind, I would die when I hit the floor thirty feet below. \\


I looked up at Jamie, intending my last words to be for him. I knew the moment he realized that intent. \\


Jamie jerked his body forward and threw himself and Scott into the dark hole between us.\\


\enquote{No!} I screamed as Scott's men scattered out the door. I skid over to the side of the hole, tripping over the smaller statue on the way.\\


\enquote{I'm here,} came a pained groan from Jamie, who was just barely clutching onto the side. Thanking every deity I knew of, I pulled him out of the hole and back into the nave. His wound was bleeding fresh blood and I knew we didn't have much time. I laid him on his back, as he started to slip in unconsciousness, applying pressure to his shoulder. A moan came from the trapdoor beside us.\\


\enquote{Help me. Please\dots  I'm hurt.} So Scott had survived the fall. I grimaced and pulled myself over to the edge to peer into the darkness below. I could see nothing but the creature was no longer screaming. My blood began to boil as I let Jameson Scott wail away his swan song. \\


\enquote{Please\dots it's staring at me, I can feel it. Please\dots name your price, I'll pay it. Just save me\dots }\\


I laughed. \enquote{Oh now, why would I do that, Mr. Scott? This is what you wanted, after all. You get to be young until the day you die.} \\


Suddenly the trapdoor slammed shut, Jamie standing over it, as the entire building began to shake. The edges around the door grew bright, like molten metal before darkening like a blown out flame.\\


\enquote{Will it hold?} I yelled to Jamie over the increasingly loud earthquake. \enquote{Is it blessed?}\\


\enquote{Some say by God himself.}\\


\enquote{I'd say that counts.} I said to myself as I tried to stand up on the violently shaking floor.\\


Jamie hoisted me up next to him and ran for the door as bit of ceiling began to cave in. The door to the church swung open of its own volition before we got there and slammed shut behind us. The church came down in a butt of dust and splintered wood. When all had settled, Jamie was barely conscious. I walked him to the car and pushed him into the passenger seat. He was out before I'd shut the door. I took one last look at the pile of rubble before climbing into the driver's seat and starting the car. I followed the same train tracks home that got us out of Deepwood when we were kids. I made it to the road without ever looking back.\\


I can tell you exactly how long Jameson Scott lived - 4 days. By the dawn of that forth day, he, and all of his inventions, abruptly disappeared from the world. There were a few I was sad to see go, like the rise of inductive charging and EyeGlass. You would have loved EyeGlass and you probably did, honestly.  Contact lenses that were actually cameras: they put GoPro out of business. I could never afford it, but you may have had one. I miss those YouTube videos. \\


Jamie spent a month recovering from his gunshot wound. After he was released from the hospital, we spent a few weeks weighing our options. In the end, we decided to hunt down people like Jameson Scott and the powers they wielded. You don't know about them, and if we have our way, you never will. Due to Jamie's time with Scott, we have some good leads. We have a lot of blood on our hands to atone for, and a lifetime to do it in. \\


Deepwood is dead; only Jamie and I even know where it is, so the town dies with us. I wouldn't try to find it if I were you - I've changed a lot of details: names of towns, names of roads. Perhaps even \textit{when}
 this all happened. I won't tell you and you don't want to know, anyway.\\


Somewhere, out in a hundred mile sea of trees and dirt lies the demon's door. It's still there, under a pile of rotting detritus that used to be a small church. The door may be found again someday, it may even be opened. But one thing is for damn sure: it sure as hell won't be because of me.

\clearpage
\section*{Stories of this series}

\begin{itemize}
    \item Story 1: The Lost Town of Deepwood, Pennsylvania
    \item Story 2: Return to Deepwood, Pennsylvania
    \item Story 3: Death of Deepwood, Pennsylvania
\end{itemize}
\end{document}