\documentclass[a5paper]{scrartcl}
\usepackage{amssymb, amsmath} % needed for math
\usepackage[utf8]{inputenc} % this is needed for umlauts
\usepackage[USenglish]{babel} % this is needed for umlauts
\usepackage[T1]{fontenc}  % this is needed for correct output of umlauts in pdf
%\usepackage[margin=2.5cm]{geometry} %layout
\usepackage{hyperref}  % links im text
\usepackage{csquotes}
\usepackage{stackengine}
\usepackage{graphicx}
\usepackage{siunitx}
\def\asterism{\par\vspace{1em}{\centering\scalebox{1.5}{%\\
 \stackon[-0.5pt]{\bfseries*~*}{\bfseries*}}\par}\vspace{.5em}\par}

\usepackage{yfonts,color}
\usepackage{microtype}

\title{Welcome to Dell: The customer service call that fucked my life (Part 2)}
\author{SeriouZero}
\date{September 17, 2014}

\hypersetup{
 pdfauthor  = {SeriouZero},
 pdfkeywords = {Reddit, nosleep},
 pdftitle  = {Welcome to Dell: The customer service call that fucked my life (Part 2)}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\\
% Begin document                                                    %\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\\
\begin{document}
\maketitle

\section*{Preface}
Hello redditors. I must say I didn't expect so many responses and I appreciate all the feedback and messages you guys have sent. A lot has transpired since my last post and I think I've figured out a lot.
If you have not read the first post please read it before reading on.
Before I start, I would like to clear up some things\dots\\


First of all the envelope that I found on my coffee table was not there when I was watching TV after I got home, so if this fucker was in my house, it had to be while I was there and yet all of the locks were still secure. As far as my previous psychiatric issues, I would like to elaborate since I know some of you were curious whether these issues considering my perception may be jeopardized. Before I moved away from my parents, I had fallen into a 'bad crowd' and experimented with drugs during my teen years. I took more LSD than intended one night and had to return home before my 9~p.m. curfew. My parents immediately took me to the hospital.
While under the influence my time in the hospital (and the psych ward that followed) was one of the most fucked up experiences I have ever had (considering I was in a hospital on LSD having people prod and question me for days on end). It was like the trip never ended and ultimately it affected my mental state for a couple years. LSD doesn't show up on urine tests for those who aren't familiar with it and since I vehemently denied having taken drugs, afterwards the doctors and my parents to came to the conclusion that I was schizophrenic. My parents weren't aware that I had taken anything but forced me out of their home and lives at this point as they had considered me 'a danger' to the well being of their perfect life.\\


Since I am considered a schizophrenic, the idea of contacting the police makes me think they may never believe me and I am gathering proof until i can show my case completely. At this point, I have not yet contacted any authorities. Now onto the events of the last day:
I woke up this morning, hoping this was all a dream. However, I soon saw the red envelope which lay next to me on the night stand. I had the day off and decided to do a little investigating. I tried to access my Dell account from home to obtain the recording, with little success. However I did find a way to track the caller ID on the call I had received yesterday. It had no name, still listed as 'call forwarding' but the number was displayed beneath. I did a reverse phone look up and discovered the number traced back to my mother. I was baffled, expecting it was yet another trick by this stalker but decided that, after years of no contact, it may be time to pay a visit to my mother.
The drive to my mother's house is about an hour away, I was cautious as I left the house; even going so far as to wear a jean jacket with several inner hidden pockets, each of which held several knives just in case. I wasn't looking forward to this visit to be honest. I hadn't seen my mother for almost four or five years and the thought of confronting her and having her treat me like a madman and an outcast only made me want to turn back. However, if she had something to do with this I was more than anxious to find out. I pulled up to my mother's house, a large ranch that was not quite 'country' yet not so 'urban', she had neighbors, but could cause quite a lot of noise without anyone hearing a thing. It was a large one story house built upon about an acre, she had no livestock however, which differed from most of her neighbors.\\


I sat in my car for about half an hour, contemplating whether I should go through with this step or not but i figured that the day I met her again face to face would come one way or another. I put one foot out of the car and almost felt she would come out of the house the moment my foot hit the ground and shoo me away. I made it up to the door, without any disturbance, making sure to look around in all directions for any suspicious characters or vehicles I may have not noticed. No one was around for miles. I slowly walked up to the door and placed my hand nervously upon the lion shaped door knocker. I knocked slowly and softly at first, almost hoping no one would hear and I could easily give up. After a few minutes, I went to head back to my car, I took three or four steps and heard the door open behind me. \enquote{Lina} someone said behind me. I almost cringed at even hearing my name after all I had been through in the past day. \enquote{Lina, you can come inside}. I turned around and saw my mother standing boldly but with a tinge of awkwardness, as though she felt the same uneasiness I did. \enquote{Mom} I replied, walking towards the door slowly, almost praying that she would simply send me away. \enquote{Well\dots how have you been} She said in a cold, disconnected manner. \enquote{Pretty good, mom. How about you?} \enquote{Well I'm OK, don't even ask about your father, he's the same as always.} she responded in her usual tone, as though she had better things to do and conversation only distracted her from her carrying on about her day.\\


My father was in an accident in his time as a police officer when I was very young and suffered brain damage as a result. He never spoke or did much, though my mom consistently treated him as though he were another 'burden' to bare. \enquote{Lina, are you going to ask me to live here?} She said, as though she were getting straight to the point. \enquote{What?} is I could utter in surprise at her ongoing monologue. \enquote{Well we have started to receive your mail. You haven't lived here for years, the fact that you are too lazy to even change your mailing address with those you transact with is just shameful}. She responded in her continuing hoity-toity monologue. \enquote{What are you talking about?!} I finally interjected. \enquote{Here} She said sternly, handing me some mail. I sifted through it, seeing letter to my dad, my mom, back and forth until finally I came to a red envelope which read \enquote{Lina} I stood, horrified, almost in disbelief.\\


I opened the letter slowly as my mom sighed in disgust, trying to shove a letter opener towards me, insisting it was barbaric to open letters without one. Inside was a white card, I opened it slowly, praying it was merely an advertisement or letter from an old friend. I opened the card, turning my head to prepare myself to turn my eyes away, and saw \enquote{Keep your neck straight Lina, your mother will notice and think you ill}.
I left quickly and raced home after assuring my mother I had no intention of seeing her again. I locked the doors, made sure every edifice of the house was tightened. And as I sat here, starting this update I looked out my window and saw \href{http://imgur.com/99g68Nr}{this}.
He has been there for over an hour now.\\


\clearpage
\section*{Stories of this series}

\begin{itemize}
    \item Story~1: Part 1
    \item Story~1: Part 2
\end{itemize}
\end{document}