\documentclass[a5paper]{scrartcl}
\usepackage{amssymb, amsmath} % needed for math
\usepackage[utf8]{inputenc} % this is needed for umlauts
\usepackage[USenglish]{babel} % this is needed for umlauts
\usepackage[T1]{fontenc}  % this is needed for correct output of umlauts in pdf
%\usepackage[margin=2.5cm]{geometry} %layout
\usepackage{hyperref}  % links im text
\usepackage{csquotes}
\usepackage{stackengine}
\usepackage{graphicx}
\usepackage{siunitx}
\def\asterism{\par\vspace{1em}{\centering\scalebox{1.5}{%\\
 \stackon[-0.5pt]{\bfseries*~*}{\bfseries*}}\par}\vspace{.5em}\par}

\usepackage{yfonts,color}
\usepackage{mystyle}
\usepackage{microtype}

\title{Repressed Memories are Meant to Stay Dead}
\author{C. K. Walker}
\date{September 05, 2014}

\hypersetup{
 pdfauthor   = {C. K. Walker},
 pdfkeywords = {Reddit, nosleep},
 pdftitle    = {Repressed Memories are Meant to Stay Dead}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\\
% Begin document                                                    %\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\\
\begin{document}
\maketitle

\begin{shadequote}[l]{Snuffy14}
It's not confusing\dots it's paranormal and terrifying. Very well written.
\end{shadequote}

\begin{shadequote}[l]{KingHabby}
Fuuuuuuuuuuck, that's terrifying. [...]
\end{shadequote}
\clearpage

This story was written by C.~K.~Walker and first published on Reddit under the
pseudonym \textit{The\_Dalek\_Emperor}. Then
Martin Thoma typesetted it professionally.\\

The work is licensed under the CC-BY 4 license.\\

This PDF and more as well as the source files are available at
\url{github.com/MartinThoma/free-books}.\\

If you want to contribute a store, images for an existing story or report
errors you can contact Martin Thoma (info@martin-thoma.de).

\clearpage

\yinipar{\color{black}W}hen I was a kid I lived in a beautiful house. My mother and my older sister were artists; they painted, sculpted and danced their way through life, challenging and inspiring each other. They created and scrapped works of art in a constant rotation. Our house was forever changing and evolving into something new like it had an organic, vibrant life of its own. \\


My memories of those days and that house are so very vivid. \\


Our family room was usually some shade of orange (my sister had painted it for me --- orange was my favorite color).\\


We had a marble bird-shaped fountain in the middle of the kitchen (which I used to splash my mom and sister),\\


There was a sculpture of a small dancing man on our landing (which I always high-fived), \\


And of course, the hallway that was painted floor-to-ceiling with fish (which I always laid on the floor to \enquote{swim} through).\\


And, finally, my favorite thing of all, a staircase that my sister had painted like piano keys (although I'm pretty sure it's only because she was in love with her piano teacher). \\


In short, my house was a magical place that the neighborhood kids couldn't stay away from. Suffice it to say I had a lot of friends.\\


Since we had the most exciting house in the county, people would always ask to come over and visit. My parents threw countless BBQs, dinner parties, open houses; just give them something to celebrate and they'd throw a party. \\


I had so many wonderful memories of my life from before the night Anna died. I had so few of the night that it happened. And, perhaps worst of all, I had no memory of the only moment that really mattered. Until I did. \\


My father owned a locksmith company with my Uncle Peter and they were out on call that night. I think mom was home in her room but I can't quite remember.  She was gone a lot in those days. It wasn't until I was older that I learned there were whispers of an affair between my mother and Samuel, the curator of a local art gallery. But that night I'm sure I remember piano music coming from her room. Anna was in bed because she had an early meeting at the gallery to unveil her newest canvas. And I was in my room as usual playing Tomb Raider on my Playstation. \\


At some point in the night I think I must have heard a noise because I remember pausing my game and cracking my door to look out into the hallway. I recall staring down the corridor toward the staircase trying to adjust my eyes to the dark. I thought there may be someone there so I came out fully into the hallway to see. I remember that for some reason I was afraid to turn on the light so I squinted down the hallway .\\


There was someone staring back at me. Someone in the dark, someone who had just come up the stairs, someone\dots I recognized. He stayed completely still, perhaps wondering if I could see him too. \\


As he stared at me I began feel scared. I wanted to run toward the light-switch but I didn't have the courage. And then, suddenly, in a single breath the figure was moving, sprinting down the hallway toward me.  Too afraid to scream, I fell over backward and scrambled into my room as I watched the figure run into Anna's bedroom. I don't remember anything else from that night. Not screaming from Anna's room. Not hiding under the bed. Not falling asleep. \\


Uncle Peter and my dad had come home together that night after finishing their call. They spent the night drinking in the garage, which was the only room my mother never touched (and the only room my father could relax in). So it was Uncle Peter that found Anna the next morning. She had been beaten to death; her head was completely caved in. I wish I didn't know that but adults talk loudly when they're upset. \\


I spent the day hiding under my bed, plugging my ears and crying.\\


My mom was hysterical; screaming and crying so loudly that an ambulance came to take her to the hospital. My father, not knowing what else to do, sent me to stay with Uncle Peter and Aunt Lydia for awhile. It was only a day later that the police showed up at my uncle's door and asked to talk to me.\\


They sat me down in the living room and my aunt brought me a glass of chocolate milk. They asked me if I had seen anything that night and I told them I had. They asked me what happened and I told them what I knew. They asked me who it was that I'd seen in the hallway and I faltered. \\


I couldn't remember.\\


They kept at me until I cried. It felt like hours. My uncle stood in the doorway watching as the detectives asked me the same questions over and over again. Was he tall? Short? Did he have long hair? Was he old or young? What was he wearing? But try as I might, I simply couldn't remember anything. All I knew was that I recognized him. The detectives tried to hide their frustration and anger but ultimately failed. At one point I was so scared of them I thought of making something up. But I didn't want to send anyone I knew to jail.\\


My parents didn't talk to me at the funeral and it was clear to me that they'd heard about my failure to identify Anna's killer. David the piano teacher talked to me, though, and he cried. I guess he'd had a crush on Anna, too. Most of mother's art friends came over with a few kind words to say. My teacher was there. Samuel the curator didn't come at all.\\


A few days after the funeral, a child psychologist came to my uncle's house. She asked me the same questions the police did, but in a much gentler way. She didn't get mad at me when I didn't know the answers, either. I heard her tell my aunt and uncle that I had repressed the memory of what I saw and that it happens sometimes when a child is involved in a traumatic event. Uncle Peter asked if I would ever remember who it was. The psychologist said that one day something may trigger it again, but not to pressure me. My uncle nodded, gravely.\\


A week after that I was sent back home. Or at least, sent somewhere that used to be home. The walls of my house were now all white or gray. The bird fountain was gone, the undersea hallway was gone, the sculpture was gone. Anna's piano stairs were now covered in dark brown carpet.  I found my mom drinking a glass of wine and painting over the stars on the floor of the entryway. She didn't look at me for another week. She didn't speak to me for a month.\\


My once bright, lively home was now the color of Anna's tombstone. I was left alone in my room most of the time. Occasionally my mother would come by and ask matter-of-factly if I remembered yet who it was that had murdered her baby girl. But I hadn't. The asking turned to pressing, the pressing to demanding and the demanding, finally, to hysteria. My father had to stop her from shaking me and screaming at me several times but I didn't mind it. They were the only interactions I had with my mom, anymore. \\


Once in a while a detective would come by to talk to me but I never had anything new to tell them. My mother took me to a renowned hypnotist behind my father's back and I woke up screaming in hysterics. To my mother's disappointment I hadn't said anything during the session and didn't remember what I'd seen while I was under. My dad was pissed when he found out. \\


I really did try very hard to remember. I lay in bed every night for four years squeezing my eyes shut and screaming at my brain to show me what my eyes had seen. But it was no use. The memory was there, I could still see the figure in the darkness. But it had no face.\\


And because I \textit{knew}
 that the person I'd seen that night was someone I knew, someone who was probably still around, I was constantly afraid. I hid from my uncle, Samuel, my mother's art friends, even my dad. \\


But worse then all of that was just knowing that I'd failed Anna. I fell asleep in tears more nights than not.\\


Eventually I was old enough to go away to college. I stopped crying at night and started drinking instead. It came to a point where I couldn't fall asleep unless I was blackout drunk.  I no longer wanted to remember what I'd seen. It had been too many years; the wounds were old and finally starting to heal. I didn't need to know the truth of what happened that night and I convinced myself it didn't matter anymore, anyway. \\


As graduation neared I was surprised to hear from my dad that my mother was planning to attend the ceremony.  I spent all of my summers and holidays on campus and I hadn't spoken to her in four years. I was hesitant didn't know what to expect.\\


When the day came, I nervously waited for my parents' car to pull up outside of my apartment. As soon as she got out of the car, my mom threw her arms around me and cried. She apologized for abandoning me when I needed her most and she begged my forgiveness. I hugged her back and told her how much I'd missed her. It had taken 18 years, but my mom was finally getting better and it was the happiest day of my life. My parents asked me to come home after graduation and live in my old room while I looked for a job. As any broke, homeless, new graduate would, I excitedly agreed.\\


I drove home on a Friday and found a surprise graduation party waiting for me when I arrived. And that wasn't even the best part. The best part was that my house was no longer shades of gray and death --- it was a menagerie of color and life again. Life that had been breathed back into my childhood home, even dad didn't seem to mind it anymore. The fountain, the fish hallway, they were all back! \\


I spent the night laughing and clinking glasses with people I hadn't seen since the funeral. David the piano teacher was there, married now, with his youngest son. Uncle Peter shook my hand and told me I'd become a fine young man. Aunt Lydia hugged me tightly. Some of mother's art friends were there, too, and they hadn't changed at all- they still talked loudly and often. \\


Close to midnight, though the party was in full swing, I decided I needed a break to just quietly appreciate how life could take you to rock bottom and then raise you back up in such eloquent ways.  I wandered around the house, quietly admiring some of my mother's new pieces.\\


I made it upstairs and found that my room had been converted into a more respectable, adult bedroom with a flat screen and a computer desk. And I was happy to see they'd left me my PS1! I peaked into my parent's bedroom, too, and admired the Saharan theme before walking down the hall to come face to face with the very last bedroom --- Anna's. I leaned my head against the closed door for a few moments and sighed deeply.\\


\enquote{I'm sorry, Anna,} I whispered before pushing the door in.\\


Anna's room was a mausoleum. It looked exactly as it had the night she'd died only the bed was made with different linens and the carpet had been replaced. All the blood covered up or cleaned away. I couldn't bring myself to go in.\\


I suddenly heard a wooden creak on my right and snapped my head toward the staircase. A man was coming up the stairs and he had paused on the landing to lean against the dancing man statue and turned to smile at me. My glass fell to the floor to shatter at my feet.\\


You'd think a repressed memory would come back to you slowly, ebbing and flowing like a wave on a beach, leaving behind tendrils of the truth with each swell. But it wasn't like that at all. As soon as I saw his face, I knew, and I remembered everything. \\


The dancing man stared up at me from beside Samuel on the landing. And even though it hadn't moved, I could feel it staring back at me. \\


The panic began to well in my chest just as they did all those years ago, when the dancing man had climbed the stairs to stare at me in the darkness.  I remember it all now. I remember, too, Anna's screams when the statue entered her room. I remember my mother's piano gently playing Vivaldi over the sounds of my sister's bones cracking and her flesh tearing. \\


I remember when the dancing man, covered in blood, appeared at my door and danced to my mother's music, his smile growing bigger and toothier every second. And I remember when he danced away, leaving a dark trail of my sister's blood behind him. I remember everything now.  \\
\end{document}