\documentclass[a5paper]{scrartcl}
\usepackage{amssymb, amsmath} % needed for math
\usepackage[utf8]{inputenc} % this is needed for umlauts
\usepackage[USenglish]{babel} % this is needed for umlauts
\usepackage[T1]{fontenc}  % this is needed for correct output of umlauts in pdf
%\usepackage[margin=2.5cm]{geometry} %layout
\usepackage{hyperref}  % links im text
\usepackage{csquotes}
\usepackage{stackengine}
\usepackage{graphicx}
\usepackage{siunitx}
\def\asterism{\par\vspace{1em}{\centering\scalebox{1.5}{%\\
 \stackon[-0.5pt]{\bfseries*~*}{\bfseries*}}\par}\vspace{.5em}\par}

\usepackage{yfonts,color}
\usepackage{mystyle}
\usepackage{microtype}

\title{Return to Deepwood, Pennsylvania}
\author{C. K. Walker}
\date{June 30, 2014}

\hypersetup{
 pdfauthor  = {C. K. Walker},
 pdfkeywords = {Reddit, nosleep},
 pdftitle  = {Return to Deepwood, Pennsylvania}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\\
% Begin document                                                    %\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\\
\begin{document}
\maketitle

\begin{shadequote}[l]{lazyirishsparkle}
I have been waiting for this for months\dots the original post was SO HORRIBLY CREEPY. Thank you so much!
\end{shadequote}
\clearpage

\yinipar{\color{black}H}arrisburg is an antiquated, yet charming Pennsylvanian town on the Susquehanna River with roots reaching back into the 18th~century. At least, that's what the tourism brochure read. I'd really have to take their word for it.  I had researched a lot of Pennsylvania townships in the last year, but this wasn't one of them.\\


I handed the brochure back to the tall, red faced girl behind the hotel desk. She sniffed loudly as she took it and unceremoniously slid my credit card back across the counter at me.\\


\enquote{Thanks,} I muttered.\\


The girl dropped a brass key on the counter which I eyed with suspicion. I hadn't seen a hotel with actual brass keys since I was a kid. I didn't know if it was my limited funds or Harrisburg's \enquote{antiquated charm} at work, but either way, it sent an involuntary shudder down my spine.\\


\enquote{Room~217. Check out's at~10.} The girl said, wiping her small, watery eyes with the back of her sleeve.\\


I picked up my luggage and shoved off to find my room. \\


Eager to be done with it, I hadn't bother to ask where to find room~217. When I finally located it on the other side of the building, I was exhausted and ready for whatever awaited me on the other side of the door. It was as you'd suspect: dated, droll and dusty. I took a short shower and spread my maps out on the painfully flat yet somehow still lumpy hotel mattress.\\


It was strange to be back in Pennsylvania after all these years. Honestly, I was just happy it was still here. I had spent years trying to pretend I'd dreamed it all. Trying to convince myself that I'd had a very vivid psychotic breakdown and I'd never actually been to Pennsylvania at all. And I might have believed it too --- if it weren't for Jamie.\\


He was as real to me as the face in the mirror. I couldn't have dreamed him up if I'd wanted to. And if he had been real, than so had everything else. The Damned Church, the Demon and the hell I'd brought down on Middlesbrough. How many more had died since then? I needed to see for myself. I needed to prove I wasn't crazy, even if doing it meant I would have to face the consequences of my actions --- the death.  \\


I stared at my notes and topographical maps until my vision began to blur. I'd been researching and preparing for this trip for a year and yet, here I was, in Pennsylvania, still with no real direction.\\


It had been thirteen years since I'd stepped foot in this state and only for one of them had I considered coming back. \\


I'd lived only half a life for  the last decade, slowly suffocating under the heavy, pungent cloak of guilt. Usually, I could escape it in Ambien laced dreams or when I was utterly black out drunk --- which is an easy order to fill when you work in a bar. But a year ago, my tricks had abruptly stopped working and it had been too long since I'd come up for air. I'd known it was time to go back.\\


I spent an hour trying to find a comfortable position on the worn-out hotel mattress. When that failed, I picked up the maps again and studied their details, though I'd memorized them all. I suppose I was waiting for something to just click, some small detail I'd overlooked that would suddenly make all the difference; a clue as clear as daybreak that had been in front of me all along. But none came and when I woke again it was buried under a pile of legal pads and maps and suffering a sore back.\\


I showered again, not trusting the comforter, and reluctantly drank the motor oil that passed for breakfast blend coffee. I packed up my research, checked out of the hotel and sat in my car watching the sun slowly brighten the populated downtown area. At least the creature hadn't made its way here; this city had a population of around~$\num{50000}$. But how many other cities with similar populations were gone because of me? It wasn't something I wanted an answer to.\\


Since I had no other data to go on, my plan was to drive to the least populated areas and see if what wasn't there would give me a clue to what had once been. Basically, I was looking for an area that by all logic should have a city --- but didn't.\\


I put the Ford Focus in drive and headed west out of town.
Half a day was spent driving to the middle of the state and another two days aimlessly driving around central Pennsylvania looking for something familiar; a mountain, a water tower, a road, \textit{anything}. But it was as if I'd never lived here at all.\\


On the fourth morning, discouraged and frustrated, I checked out of yet another shitty motel. I only had three more days before my flight back to Arizona and so far the trip had been utterly useless.\\


The man at the front desk took my key and gestured toward the \enquote{continental breakfast} of prepackaged muffins and 
horse-piss coffee.\\


\enquote{No thanks,} I grumbled.\\


\enquote{Wheryeadded?}\\


\enquote{Huh?} I raised an eyebrow at him.\\


\enquote{Where ye headed?} He repeated, more slowly. I couldn't place his accent, the closest I could get was maybe southern.\\


\enquote{Oh, ah, I don't know.}\\


\enquote{Well, if yer 'eaded down the~320, gas up before ya leave town. There ain't no gas stations or towns between here and Lannenburg.}\\


\enquote{But\dots that's like 90~miles away.}\\


\enquote{Yep, never understood it myself. People get stuck on that road all the time, blowin' tires and runnin' outta gas. I don't know why the government hasn't done sumthin about that.}\\


\enquote{Because they're broke!} Someone yelled from the back office.\\


\enquote{Yep, that's it, most likely. The state ain't got money for it.}\\


\enquote{I'll get gas before I go,} I promised and received an approving nod in return.\\


I practically ran out the door. For days I'd been looking for the out-of-place, the not-quite-right, the bizarre and this was\dots well, it was odd, at least. And it was all I had.\\


I gassed up before I left town and followed the signs to the~320. As promised, it was nothing but dark asphalt for miles. No exits, rest stops, signs or ever mile markers. This was it. It just had to be.\\


Since there was no one else on the road, I drove well under the speed limit taking in every detail. Eventually I began to notice that periodically there would a gap. Not in the foliage, but in the coloring of it. \\


Every so often, a grove of trees would be duller, sicker. It was something you'd only notice if you were looking for it. So the creature, as I'd taken to calling it, could technically \enquote{give life} (in the process of filing in the hole of previous existence) but not very good life.  The fauna in these spots was  weaker and bore dull, almost muted coloring.\\


I continued noting these spots until I couldn't count them anymore. These had likely been cities or homes of people with lives, families, futures, all taken from them because of me. I felt the panic begin to claim the edges of my vision and quickly popped a Xanax. My panic attacks had become unbearable after Middlesbrough. I suffered from them still. The edges of my vision got hazy and I was able to relax a fraction.\\


At some point, I processed the presence of the dilapidated railroad tracks running parallel to the road. I'd noticed them early on, but my mind had hidden the significance of this until now. They may not have been \textit{the}
 tracks, but to me, it was a sign that I was on the right track (so to speak).\\


I was close. I had to be. And if Lannenburg was still there, that meant the creature hadn't made it that far yet.\\


I somehow knew --- like I knew that I'd once lived somewhere off this road --- that the creature had been moving north. But it hadn't claimed Lannenburg yet. Why? Was it satiated? Had it left the area? Or was it just slow moving? Whatever the answer, I felt I'd learn it in Lannenburg.\\


As I reached the outskirts of the city, I saw my first road sign since I'd merged onto the~320.\\


\textit{Lannenburg}
\\


\textit{Next 17 exits}
\\


I decided to take the exit that would get me into the heart of downtown Lannenburg, if there was one. I hadn't researched the city of Lannenburg either, thinking it was too far north to matter. And yet, here I was.\\


The downtown area began to take shape off my right like the Damned Church had in the woods so long ago. But I didn't need spray paint to find my way anymore. I exited the highway and drove around the cityscape until I found a centrally located hotel that I could afford. I parked and heaved my bags out of the car, hoping they had vacancy.\\


They did, I was told by the overly flirty college senior behind the front desk, slinging his guitar behind his back.\\


\enquote{Do you have Wi-Fi?} I asked as he handed me the key card.\\


\enquote{We do, but there's a \$10 a day charge for the password.}\\


\enquote{Damn.} I was on an extremely tight budget.\\


\enquote{But I can give it to you for free if\dots } He let his voice trail off suggestively.\\


\enquote{If what?} I raised a skeptical eyebrow at him.\\


\enquote{If you let me write a song about you---} he righted my credit card receipt so he could read it \enquote{--- Caitlin.}\\


I sighed. \enquote{Ok, yeah, fine.} At this point there wasn't much I'd say no to. I was going on four days of restless sleep.\\


He eagerly gave me the password and I retired to my room, first floor, thankfully. I took out my shitty laptop, connected to the hotel's equally shitty wifi and pulled up the Wikipedia page for Lannenburg.\\


It was a larger city for this part of the state, around $\num{55000}$ residents, mostly due to the fact that Lannenburg hosted a state university. It was a progressive, young, educated town filled with hipsters and young professionals. Where to even begin?\\


I threw my notes, my phone and my GPS in my backpack and decided to start with the front desk of the motel, much to my own dread.\\


The college kid who'd checked me in was strumming chords on his guitar and softly humming.\\


\enquote{Excuse me.}\\


He looked up at me and winked. \enquote{You're pretty eager, foxy lady, and I like that. But songs take time to write, even for the most talented---}\\


\enquote{Yeah, actually, I was just wondering, where can I find the university?} I interrupted, suppressing an eyeroll.\\


\enquote{Mama, this whole city is a campus! I mean, where'd you wanna go? You a new student? I'll show you around. I get off in---}\\


\enquote{No, I'd like to find the, ah, the\dots} This had been a horrible mistake. \textit{Think of something quick, genius.}
 \enquote{\dots admissions office. I need to talk to admissions.}\\


\enquote{Ah, well, that's about half a mile down Rooker Street. That's the one---}\\


\enquote{---running in front of the building, got it, thanks.}\\


He started to say something else, perhaps which way to go down Rooker, but I was already out the door. Not knowing what else to do --- and wanting to get as far from the poor kid as possible --- I picked a direction and started walking.\\


Even though it was May, I was still freezing. I hadn't been built for the far north and my blood had thinned out living in Arizona. With my backpack and my age I probably would have passed for any other college student on campus --- if it wasn't for the hoodie I had pulled tightly around me.\\


I envied them all. Kids just a year or two younger than me going to classes, hanging out with their friends, making  stupid yet amusing mistakes. It could have been me, once. But I hadn't grown up like them. Even since Middlesbrough I had struggled with school and life in general. I couldn't focus, I couldn't laugh; I became a sarcastic, guilt-ridden introvert and I lost all my friends. Then my dad died and my mom started to look at me differently. I stopped talking about Middlesbrough the day I heard the word \enquote{hospital} whispered to my mother by a psychiatrist.\\


Even though I stopped trying to prove it had all been real, my mother never really saw me as her little girl again. I'd moved out at~18 and lived alone for years, working in an English pub, trying to forget how many people were probably dead because me --- including Jamie, the knife that dug the deepest.\\


I walked the downtown area all day. I didn't know what I was doing, where I was going, who I should approach, or what I should ask them --- I just knew I was in the right place. I'd been drawn here for a reason; I felt it in my gut. This was where I was supposed to be. But for the fifth time in as many days I had to ask myself: What now?\\


I suppose I could have spent days wondering around Lannenburg. I could have left empty handed and never known what happened all those years ago. I could have never found him. But, as fate would have it, it only took half a day to find what I was looking for.\\


It was well past noon and I had stopped at a small caf     to eat a sandwich. Since the restaurant was packed wall to wall with students, I went outside and leaned against the brick wall by the door.\\


I suppose I noticed it because it was so brightly colored. Or maybe because it was the only piece of litter I had seen all morning. Or, just maybe, it was simply because I was supposed to. But for whatever the reason, when a bright red flyer blew past my feet, I reached out to step on it.\\


Curious, I bent down to pick it up and read the heading:\\


\textbf{Tethen History Museum --- Lannenburg, PA}
\\


\textbf{Upcoming Exhibitions}
\\


\textbf{13th--14th Century Judeo-Christian Relics and Artifacts}
\\


Below that was a blurb about the museum, nothing too interesting. And below \textit{that}
 was a description of the exhibits to be unveiled.\\


I skimmed down the list quickly seeing little of interest --- until the very bottom.\\


\textit{Statue of the Demon Metaraxes}
\\


My mouth fell open. It was too much of a coincidence, nothing to be ignored. I checked the date on the flyer. May~2nd~2014: 3~weeks ago. I threw the rest of my sandwich in the trash and took off. I'd seen the museum that morning and I knew where exactly where to find it.\\


It was only three blocks away and I got there in under five minutes, flew up the building steps and stumbled straight to the cashier window.\\


\enquote{Student ID, please.} The old man said, flatly.\\


\enquote{I'm not a student.}\\


\enquote{Well, you look---}\\


\enquote{How much?}\\


\enquote{Eleven dollars.} I was gladly willing to pay.\\


I didn't stop to grab a map, instead joining a tour group already in progress. The museum, I could tell, was a veritable labyrinth and I certainly didn't want to get lost, not in here, not with that thing --- if indeed, it really was what I half hoped, half dreaded it could be.\\


It took the longest twenty minutes of my life, but we finally came to the room I'd been waiting for.\\


\enquote{Now behind this door is our newest exhibition on ancient Judeo-Christian artifacts. Please do not try to touch anything or you will be escorted out. These pieces are centuries old and may be damaged by the lightest touch.}\\


\textit{If you have behind that door what I suspect you do, than I 
highly doubt it.}
\\


\enquote{Also, please no flash photography.}\\


My heart beat a million miles a minute as the docent opened the double doors and my group was shuffled in. I lingered toward the back, letting everyone go in front of me.
I had come thousands of miles and done months of research to find that statue, to prove I wasn't insane, yet when the time came to possibly face my nightmare, I was hesitant.
Finally I was the last and the docent had to wave me in with a polite but impatient hand.\\


There were about a hundred things in that room. All sorts of things, really: sculptures, paintings, pottery, even other statues. But I only had eyes for the thing in the middle.\\


It was larger than I remembered. Not the twelve feet I had guessed, it was actually closer to twenty. But every detail of its face and body was exactly as I'd remembered, though it was positioned differently now.\\


In the church, all those years ago, it had seemed as if it was standing, waiting yet content. But now it was positioned as if ready to leap off the stone square that it stood upon, its tail was paused in midair, instead of wrapped idly around it's legs as it'd been before.\\


Though it was taller than I'd remembered, I could at least see its face this time. It wasn't particularly scary, just an empty, stony face, far from the hungry, animated one it became when it woke.\\

% TODO Add Image of the demon on statue

And like the crucifixion statue in the Damned Church, it had eyes only for me.\\


The rest of my group took photos, oo-ing and ah-ing as they made their way around the room. I stood directly where I was, against the now closed door, going no further. The docent walked around the room, discussing notable pieces of the collection and I only moved from the door when she finally stood before the creature.\\


\enquote{And, finally, the jewel of this exhibition: a granite statue from the 14th~century. This is a representation of Metaraxes, a lesser known demon of Christian mythology. It is unique in its size as well as its crisp detail, especially for something so old. Our conservationists are unable to discover its place of origin or creator.}\\


I edged closer and closer to the red velvet rope. Its eyes followed my every step. The room seemed to grow hotter. \\


The docent moved to the side so people could get pictures in front of the statue. Though I couldn't blame them, I barely kept from yelling. This was madness.\\


The stone platform on which the demon stood was covered in red velvet, which pooled at the creature's feet. It hid the words inscribed on the front of the granite stand that Jamie and I couldn't read those many years ago.\\


The docent droned on about nothing and I read the description plaque.\\


\textit{14th~Century representation of the Demon Metaraxes}
\\


\textit{Artist Unknown}
\\


No shit.\\


And then I saw what I didn't know I'd been looking for --- the triangles. The symbols I would never forget, etched into the doors of the Damned Church. And once I found one, I found another and another. There were half a dozen of them. \textit{So that's how they're doing it.}
 They (whoever \enquote{they} were) had placed wards all around the base of the creatures stand. \\


The museum not only knew what this thing was, they knew about the sigils on the doors of the Damned Church and were \textit{using}
 them to trap the statue here. The revelation was like a punch to the face. Someone was aware of what this statue really was and was blatantly risking innocent lives anyway. It was insane.\\


In a panic, I turned to find the docent and saw her conversing politely with an elderly couple. \\


\enquote{Excuse me!} I interrupted loudly. \\


\enquote{Yes?} She failed to mask her irritation at my rudeness.\\


\enquote{Where did the museum acquire this statue?}\\


\enquote{This piece is on loan from a private collection.}\\


\enquote{Whose?}\\


\enquote{It belongs to Jameson Scott.} The docent, feeling the exchange was over, turned back to finish her conversation. \\


Jameson Scott. I knew that name, but from where? As our group began to move out of the room I took one last look at the creature --- Metaraxes --- and shuddered. Its eyes had never strayed from me. I took my phone out and pulled up a Wikipedia page on Jameson Scott. I had to know who could be this stupid.\\


He was young --- my age --- but wealthy, had his own company and well known in the tech industry for multiple inventions. The words \enquote{brilliant}, \enquote{pioneer} and \enquote{industry leader} were scattered throughout his Wikipedia page, which had no picture. At the end of the article, under \enquote{Personal Life}, was a short paragraph about his interest in symbolism and ancient artifacts.\\


I shook my head as my group was herded into the museum's gift shop. What did he want with the statue? How had he acquired it? And how did he know about the wards? None of it made sense. I wandered through the gift shop idly picking up trinkets and wondering just what to do. Should I warn the docent? The curator? Or did this Scott person know what he was doing.  Were the wards enough? Somehow, I didn't think so.\\


\enquote{Are you going to the lecture tonight?} Some one asked from behind me.\\


I swung around, my backpack nearly taking out a postcard stand as I did.\\


\enquote{Oh! Sorry, I thought you were someone else.} The redheaded girl turned to leave.\\


\enquote{What lecture?} I asked before she could get away.\\


\enquote{The lecture our guide was talking about?} I stared at her blankly. \enquote{Jameson Scott's lecture on the exhibit?}\\


\enquote{He's in town?}\\


\enquote{Yeah, that's what she said,} the girl said, flippantly. \enquote{You should go, he's really hot.}\\


She turned to leave.\\


\enquote{Wait --- where is the lecture again?}\\


\enquote{The auditorium in the history building? Building E?} She said, as if I should have known. And I guess she wasn't wrong. I was only a few years older than her and I looked like a college student. Apparently everyone thought so.\\


\enquote{Thanks!} I yelled after her as she walked off with her giggling friend.\\


I would definitely be there. I had a few things to say to this guy and I wasn't leaving Pennsylvania until I did.\\


I sat in the back of the auditorium, as was my custom. The room was filled wall to wall with people, faculty and students alike. An empty podium sat in the front and a tall, blonde haired security guard stood to its left. He had a gun on his hip and his hands were folded behind his back. Maybe he wasn't a security guard after all. I was pretty sure state campuses were gun free, which meant he was with somebody important. Jameson Scott, no doubt.\\


The guard stared straight ahead, his eyes boring a hole into the wall behind me. Lots of things about him made me uneasy.\\


The murmurs and whispers died down a moment later when a thin, attractive man walked purposefully onto the stage.\\


\enquote{Good evening,} he began. He graced the room with a smile that couldn't fool me. The emotion didn't quite reach his eyes; if anything he looked like the most stressed out and tired 25~year old I'd ever seen.\\


\enquote{My name is Jameson Scott. I am here to speak to you tonight about a few ancient and interesting items I have collected over the years. I'm sorry, but I will not be answering questions about my company, our newest patents or my personal charities.}\\


\textit{Easy, Christian Gray.}
 I rolled my eyes.\\


There were a few disappointed groans from the audience but Jameson Scott smiled and directly a flirtatious wink at no one in particular. He was an alarmingly charming man.\\


\enquote{I have been interested in ancient relics, particularly those of religious significance, for many years. Since I was quite young, actually. A somewhat traumatic experience played the catalyst and I've been studying and collecting ever since. I'll begin with some of my more well known pieces and then move on to the more exotic. }\\


Scott began his lecture on a bowl from Mesopotamia that was supposed to bestow on the user unnaturally long life --- as long as you drank from it only water siphoned from the bottom of the Euphrates River. He spoke extensively about several other, equally uninteresting, artifacts before finally coming to the only one I cared about --- the statue.\\


\enquote{Please study this photo for a minute.} Scott clicked to the next slide in his sideshow and the demon statue appeared against a blood-red background, as imposing and terrifying as it was in real life. A blanket of heavy, uncomfortable air descended on the room as people averted their eyes from the screen and mumbled, uncertainly. I didn't take my eyes off of it.\\


\enquote{This is the piece I spent most of my life trying to locate. May I introduce to you, the demon Metaraxes.} He paused for a minute and clicked to the next slide, a Dante-esque depiction of Hell. \\


\enquote{Metaraxes  belongs to the second hierarchy of demons, though he is virtually unknown --- and this is simply because of his nature. Metaraxes doesn't kill or possess. He doesn't vie for power, bring darkness into the hearts of men or try to influence innocence.  Metaraxes eats. But he eats more than the flesh of man, he eats their homes, their histories and their souls. If you were to be eaten by Metaraxes it would be as if you'd never existed at all. No one would remember you and the now empty piece of life you had carved out for yourself in the world would fill in as if you were never there. Everything that was you or ever would be you is gone.}\\


Jameson Scott paused artfully to let his words wash over the audience; every soul in the room hanging on every syllable. I suppose it really was quite interesting, if you didn't know the heartbreaking truth of it --- which I knew he \textit{did}
. For someone hailed as a \enquote{genius} it seemed utterly reckless of him to romanticize all this.  I crossed my arms and slumped lower in my chair. When this was over, one way or another, Jameson Scott and I would be having a conversation. \\


\enquote{And this is why Metaraxes is an unknown. There is no one to speak his name or his deeds, alive or dead. Or there wasn't, for many centuries.}\\


\enquote{At some point in history, Metaraxes grew tired of being unknown and un-worshipped. He proclaimed that those who prayed to him and brought him sacrifice would not only be spared and but also given gifts of everlasting youth and resilience --- that which he had stolen from others. It is believed that several ancient civilizations took him up on his offer; they sang his songs, built his temples and created beautiful artwork in his likeness --- such as the one in your museum --- to praise the demon and reap his gifts.}\\


\enquote{And this would have gone on for many years until a name was called that refused to be sacrificed. Metaraxes choose his tribute selectively but eventually a name would come up of someone rich or in power and that person would maneuver out of it, or simply commit suicide. In these instances, Metaraxes would grow angry and eat the city and all the people therein, leaving no trace that he, or they, had ever existed. This would have happens many times over the centuries.}\\


Now this was interesting. The creature could be tamed, like a pet, and as long as you gave it the treat it wanted, you would be not only saved but rewarded. \\


\enquote{Something else to consider is that no one ever knew how often Metaraxes called a name. Since the person would be absorbed by the demon, no one would ever remember they had existed at all. It could have been one person a year or five a day and no one would know but the demon himself.}\\


\enquote{You will find mentions of Metaraxes scattered in religious texts dating back as far as 1700~BC but this statue is rare in that it is the only known likeness of him ever to be found.}\\


Jameson graced the many hands in the air with another tired smile and said, \enquote{I'm sorry but no questions, tonight. If you haven't yet had a chance to see the statue of Metaraxes, I encourage you to experience it before it is shipped to New York next month.}\\


Then, without any ceremony at all, Jameson Scott simply walked off stage and the lecture was over.  His security guard, who I realized was more likely a bodyguard, stepped forward to block several girls who jumped the stage to follow his boss. With him busy, I knew I had a chance.\\


As the throng of people pressed forward to the upper exits, I fell back and went out the rear. I sprinted out of the building and rounded the corner hoping to see what I'd gambled was there.\\


And it was. Jameson Scott was climbing into the back of a white SUV when I spotted him. He glanced in my direction at the sound of his name but then shut the door and rolled down the window as the SUV began to pull away. I threw a Hail Mary.\\


\enquote{Your wards on that demon will never hold!} My voice echoed down the alleyway.\\


The brake lights came on immediately, but no one exited the car. Taking it as an invitation, I ran up to his window.\\


For a mere 25~years old, he sure looked like he'd seen some shit. His lined, pale, yet attractive face no longer carried a tired look, but a surprised one. I bent over to catch my breath.\\


He didn't speak, but opened the door and scooted over. I climbed in.\\


\enquote{Who may I have the pleasure?}\\


\enquote{Caitlin Ross,} I held out a shaky hand. His surprise seemed to turn to shock.\\


\enquote{Caitlin Ross.} He said slowly, with a strange inflection of reverence.\\


\enquote{Yes,} I said, exasperated. \enquote{I'm Caitlin Ross. And your wards --- they're bullshit.}\\


He didn't even bother to ask how I'd known, which in turn, bothered me. He simply tapped the seat in front of him and his driver let go of the brake.\\


\enquote{Those wards have held for six years, Miss Ross. I assure you, they'll hold.}\\


\enquote{You have no idea what you're dealing with here.}\\


\enquote{Oh, I assure you I do.} There was a hard, yet sad edge to his voice that suggested  personal tragedy. I wondered if I'd misjudged him after all. \enquote{My apartments are only a block away. Perhaps we should speak more in my study. This isn't a conversation for anyone to overhear.}\\


I noted the finality in his voice and, nodding, sat back in my seat. As long as I got to say what I'd come to say, I didn't care where we went. \\


We were let off at the corner where several men in his personal detail were already waiting. Scott escorted me into a private entrance and private elevator with only one button marked \enquote{Penthouse}.\\


As soon as the elevator doors opened, one of his men ushered me into his cavernous study and the door was shut behind me. For whatever reason, Jameson entered from a different door a few minutes later, followed by his head bodyguard who'd been at the lecture. This one didn't like me one bit, barely concealing irritation and shades of panic when he saw me. He was older, clearly over 30, with dark blonde hair and a square jaw.\\


Jameson sat down behind his desk while I continued to stand. He gestured to an empty seat in front of him, but I shook my head. He gave a \enquote{suit yourself} shrug and turned to his bodyguard, whose eyes continued to bore angry holes through me as they did everything else he looked at. This was quickly becoming enemy territory.\\


\enquote{Scotch for me, Bannock. Anything for you, Caitlin?}\\


\enquote{Ah, no thanks\dots } I mumbled as the guard --- Bannock --- raked his hair back from his forehead in exasperation, I assumed at Scott's familiar use of my first name. \textit{I'm no threat to your boss, buddy, if anything he is a threat to everyone else.}
\\


I returned his icy glare, never wavering until his lips grew into a thin line and he curtly nodded to Jameson and left the room.\\


\enquote{First,} Scott begin, \enquote{I want to establish---}\\


\enquote{Do you have any idea what you're doing?} I asked, suspending all platitudes.\\


Jameson leaned back cautiously in his chair, giving me a casual \enquote{go-on} gesture.\\


\enquote{Why would you bring that thing to a populated city? Why would you put it on display for all to see and touch? What sort of arrogance allows you to think that you could control it with a few poorly copied sigils?}\\


He had made no move during my short outburst other than to tent his fingers and stroke his jaw with his thumb.\\


\enquote{Which question would you like me to answer first?}\\


Just then the one called Bannock opened the door with a little too much force and brought his great lord and master a scotch. He turned to stand beside Jameson's desk, which seemed a natural and familiar spot for him.\\


\enquote{You may go, Eric.} Jameson clipped without so much as looking at him. The guard didn't move and I continued to stare daggers at him. We engaged in our own little personal, silent standoff. He, like the statue, had eyes only for me, and they were filled with rage and fire.\\


\enquote{He can stay,} I ground out, finally. Let him know I'm not afraid of him. If he was grateful for my help, he didn't show it.\\


\enquote{As you wish. Your question?}\\


I slid my eyes reluctantly back to Jameson. \enquote{How did you get it?}\\


\enquote{I bought it from the government.}\\


\enquote{The government had it?} I asked, incredulously.\\


\enquote{The state of Pennsylvania. It appeared on government land, in the middle of nowhere, according to the surveyor who found it. They shipped it off to PSU who dated and appraised it and then they put it up for auction.}\\


\enquote{They just \textit{sold} it to the highest bidder?}\\


\enquote{Yes and why not? It's just a piece of granite to them and they needed the money. The state of Pennsylvania is suffering its own financial crisis. Though I suppose that's what happens when in essence 20\% of the state just stops paying their taxes. It's a curious thing.}\\


I winced. He didn't need to elaborate.\\


\enquote{Why did you buy it?} I demanded.\\


\enquote{Because I have personal history with Metaraxes. He has taken from me.}\\


\enquote {He's taken from me, too, but I'm not parading him around in public, risking people's lives, their \textit{souls} according to you.}\\


\enquote{If you listened to my lecture, you would know why I do that.}\\


I remained silent. Jameson sighed and leaned forward.\\


\enquote{You're right, Caitlin. The wards won't hold him, not forever, and we don't know what will. The only reason they're holding now is because I'm \textit{giving} him what he wants.}\\


I scoffed. \enquote{You assume that being exhibited in a museum satisfies the creature's desire for worship? And you're willing to stake people's lives on that?}\\


\enquote{I am. That creature has not moved a millimeter since he came into my care. I've employed teams of symboligists and demonologists to research, test and advise me on the safest course of action. And for our efforts, the statue has remained dormant.}\\


\enquote{Yes, but it's not dead. You're going to kill someone, someday.}\\


Jameson sprung up from his desk and was in front of me before I even had a chance to take a step back. His bodyguard took an almost involuntary step toward him but it was too late. Jameson was only inches from me and much more intimidating at eye level. Bannock seemed uneasy and ready to pounce if I tried anything. I didn't.\\


\enquote{What would you have me do, Caitlin? Would you like to take custody of it? What would you do with it? Tell me, and I'll consider it.}\\


\enquote{Destroy it!} \\


He gave a sad, desperate bark of laughter. \enquote{Don't you think I tried that? Don't you think the first thing I did when I acquired it was try to kill it? I tried to incinerate it, hit it with a wrecking ball, I even ran it over with a tank. It won't be destroyed by any tools of man. And, believe me, Caitlin, I paid dearly for my attempts,  almost everything I love is gone.}\\


\enquote{Then I'd put it back where it came from.} If the church was even still there and \textit{if}
 I could find it.\\


\enquote{No one can do that.} He laughed.\\


\enquote{Who did it kill? Who that you loved?} I don't know why I cared so much, but I couldn't let it go. I had to know.\\


Scott took a step back but held his ground. \\


\enquote{She was\dots she\dots } He trailed off.\\


\enquote{And just how did you escape the creature when it came for \textit{you}}\\


This question hit him physically,  like a bullet. He leaned back against the desk,  suddenly weaker, defeated and less imposing. Bannock visibly relaxed, his hand sliding off the handle of the gun I hadn't noticed was still holstered in his belt.\\


\enquote{That is a story for another time.}\\


\enquote{Fine.} But I wasn't backing down.  \enquote{Then why you? Why are you the person who is qualified to own the statue?}\\


\enquote{Because I've seen it's face. My fate is bound to it as surely as yours.}\\


Jameson Scott rubbed his face in genuine exhaustion. If he hadn't been speaking the truth, than he was a damn good actor. He looked up at me, finally, from hooded eyes that burned with some intense, unnamed emotion.\\


\enquote{And who did it take from you?}\\


\enquote{Jamie.} I had nothing to hide and I wouldn't disrespect Jamie by hiding the truth. I raised my chin a little higher and crossed my arms. Scott's expression had turned milder, almost pensive and a sad smile graced his handsome face. The tension in the room abated, though Bannock was looking at me intently, his expression unchanged since the moment he'd walked into the room. \\


When Scott didn't reply, I decided it was now or never.\\


\enquote{I want to see it.}\\


\enquote{No,} he replied, quietly.\\


\enquote{Alone.}\\


\enquote{No!} This time both Jameson and Bannock had spoken at the same time. I'd known he wouldn't let me go --- he'd never let me near the statue again. I'd assumed this before I'd even met him, which is why I'd swiped the museum keycard off his desk as soon as I'd had the opportunity.\\


\enquote{Why not?} I asked him, anyway.\\


\enquote{Because he knows you.}\\


\enquote{And you know he could break the wards if he wanted to.}\\


\enquote{No, he could never get past the wards. They are perfectly drawn and blessed as they should be. But I wont risk your life.} Jameson Scott suddenly seemed battle-weary, so much older than his 25~years.\\


\enquote{Don't even try it, Caitlin,  he will take you if you do, and the only one who will ever remember you\dots is me.} His plea was multilayered, intricately woven with threads of both deceit and familiarity. Once again, I was put ill at ease. There was only one more thing I wanted from this room.\\


\enquote{Who did it take from you and how?  Tell me that and I'll leave Lannenburg in the morning and never come back.} It was lie, but I was curious.\\


Jameson's eyes shifted to mine, perhaps to gauge if I meant what I said. He must have believed me, because his gaze drifted to the window and he answered my question.\\


\enquote{I took her from myself.} It was an unsatisfying answer.\\


\enquote{Now leave,} commanded his bodyguard before I'd had a chance to reply. Jameson stared at me as I took a step back from the desk. His eyes were again pregnant with an emotion I couldn't name, but it tread a line between longing and insanity.  Perhaps desperate desire, perhaps insane desperation. Perhaps something in between.\\


\enquote{I will walk her out.} Bannock bit as I made my escape out the door. \textit{God, anyone but him.}
\\


\enquote{No, I need you here, Andrews will see her out.} The door closed behind me and I heard no more.\\


Andrews turned out to be an older man with a bald head and a white beard. He met me at the elevator and escorted me all the way to the ground floor, saying little.\\


\enquote{Do you need a ride somewhere?} He asked as we stepped out into the street.\\


\enquote{No, I can walk.} He said no more, just turned around and let the private door shut behind him.  Nice of him to ask, at least.\\


As I walked back to the museum, I had time to wonder just what in the hell I was doing. Why didn't I listen to Scott and just leave? What did I hope to gain by seeing that thing again? Couldn't I just trust that he seemed to have everything under control? Scott had the resources, the money, the people, and, most importantly, the motivation. He had lost someone too, after all, someone he loved, though how that had come to pass was not clear. \\


But I knew I had to see it again. Perhaps I could prove to him just how dangerous that thing was, regardless of the precautions he was taking. I needed to convince him to take the statue off display before more people died. It was madness, having it here. He was exposing innocent people, to a \textit{demon}
 on a reckless gamble. If I could make the statue move just an inch or two, maybe even a turn of it's head, it was be on the museum security tapes and I could prove the thing wasn't truly dormant. I read him as a pragmatic, reasonable man --- he would remove the exhibit at once. I trusted that much, didn't I? \\


Once again I pulled up Jameson Scott's Wikipedia page. All I knew was that he was  a pioneer in the tech industry, rich as a Rothschild and interested in 14th~century Judeo-Christian artifacts. It didn't fit. It just didn't\dots unless Jameson Scott was telling the truth.\\


But even if he being honest about his past, Scott was still lying to me about something. Like everything else in the last week, I would have to trust my gut.\\


I arrived at the museum and walked around the giant building looking for the gift shop. At that moment I knew two things: the statue's room was next to the gift shop --- and museums usually had nighttime security.\\


I slid Jameson's card through the reader next to the door and a light flashed green while the door emitted a soft click. I pushed it open and peered into the empty giftshop. Dim overheard lights gave the room an eerie and foreboding glow. \\


The room reminded me of another room from over ten years ago, a nave, darkened by dirty windows and a muted, setting sun. I was younger then, more innocent, and I'd had Jamie then.\\


What I wouldn't give to have him with me, now.  What would he say? Would he trust Scott? Would he attempt to stir the creature for the greater good? Or would he say I was stupid for risking my life? Jameson was convinced the wards would hold. Would Jamie have been, too?\\


Whatever happened, I hope I didn't fail him.
\clearpage
\section*{Stories of this series}

\begin{itemize}
    \item Story~1: The Lost Town of Deepwood, Pennsylvania
    \item Story~2: Return to Deepwood, Pennsylvania
    \item Story~3: Death of Deepwood, Pennsylvania
\end{itemize}
\end{document}