\documentclass[a5paper]{scrartcl}
\usepackage{amssymb, amsmath} % needed for math
\usepackage[utf8]{inputenc} % this is needed for umlauts
\usepackage[USenglish]{babel} % this is needed for umlauts
\usepackage[T1]{fontenc}  % this is needed for correct output of umlauts in pdf
%\usepackage[margin=2.5cm]{geometry} %layout
\usepackage{hyperref}  % links im text
\usepackage{csquotes}
\usepackage{stackengine}
\usepackage{graphicx}
\usepackage{siunitx}
\def\asterism{\par\vspace{1em}{\centering\scalebox{1.5}{%\\
 \stackon[-0.5pt]{\bfseries*~*}{\bfseries*}}\par}\vspace{.5em}\par}

\usepackage{yfonts,color}
\usepackage{mystyle}
\usepackage{microtype}

\title{Paradise Pine}
\author{C. K. Walker}
\date{January 15, 2014}

\hypersetup{
 pdfauthor   = {C. K. Walker},
 pdfkeywords = {Reddit, nosleep},
 pdftitle    = {Paradise Pine}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\\
% Begin document                                                    %\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\\
\begin{document}
\maketitle

\begin{shadequote}[l]{toshietosh}
When the stick man started running up the stairs my heart skipped a fucking beat. Great story, really well written.
\end{shadequote}

\begin{shadequote}[l]{jmfkm2}
I could really see this as a movie. I realize that the story is true, and can be negatively affecting you, but this is well written and would be a horror movie that I would enjoy. If you are going to be thinking about it the rest of your life, you may as well make some money off of it.
\end{shadequote}

\clearpage

This story was written by C.~K.~Walker and first published on Reddit under the
pseudonym \textit{The\_Dalek\_Emperor}. Then
Martin Thoma typesetted it professionally.\\

The work is licensed under the CC-BY 4 license.\\

This PDF and more as well as the source files are available at
\url{github.com/MartinThoma/free-books}.\\

If you want to contribute a store, images for an existing story or report
errors you can contact Martin Thoma (info@martin-thoma.de).

\clearpage

\yinipar{\color{black}A}bout five years ago my husband and I decided to spend Thanksgiving at a cabin up north. We planned on starting a family the following year and so we wanted one last romantic holiday with just the two of us. We found the place online through a website we've used in the past and booked it for a week. The cabin was located outside of Pinetop, Arizona and the owner warned us that it can be hard to get back to in the winter because of the snow. The property was 13~miles from the nearest town and 4~miles from the nearest paved road. Aaron and I weren't worried, however, since our jeep had snow tires and we were also bringing tire chains. \\


We arrived on a Friday afternoon. We had made excellent time on the drive as there was actually very little snow on the ground. We decided to take a tour of the cabin before we unloaded the car. The cabin, named Paradise Pine, was three stories tall and built into the side of a mountain. The top floor was simply the master bedroom, which was connected to a second story patio-balcony via a sliding glass door. The front door was located on the ground floor, along with the kitchen and living room, and the basement housed a washer, a dryer and a wood furnace that heated the cabin through a large pipe that extended up through all three floors. \\


Even though the views through the bay windows were beautiful, the first thing we noticed when we walked in was that the cabin hadn't been cleaned. Often times with very rural properties, the owner will offer to waive the \$150 cleaning fee if you are willing to clean the place yourself before you depart. Most guests opt to do this, but in the rare occurrence they don't, the owner sends a cleaning crew.  The previous tenants in this cabin had clearly decided not to clean, and also not to inform the owner that they were leaving it dirty. 
Since it was a holiday and a snowstorm was forecasted for early next week, we decided to clean the cabin ourselves and ask the owner to reduce our bill when we left the following Friday. We brought everything in from the jeep and got to work with dishes and laundry. Afterwards, we made an easy dinner, opened a bottle of wine, and played a few games of billiards on the pool table in the living room. \\


The temperature started to plummet at around six in the evening and I asked my husband, Aaron, to go down and light the furnace in the basement. I went up to the bedroom to wash my face and change into warmer clothes. The bathroom connected to our bedroom was oddly door-less, had a broken mirror and a torn-down shower curtain. \textit{Wow, there's been some cowboys in here.}
 They hadn't even bothered to pick the glass up off the floor before they left. I did so carefully, regretting the stupidity of the drunken idiots who must have stayed here the week before. I took a few photos with my phone and planned to send them to the owner when we got back to town on Monday. I certainly didn't want to be charged for damage inflicted by the previous tenants. \\


I met Aaron on the ground level and told him about the bathroom. \\


\enquote{Well, that's not the only thing that's broken. The light's out in the basement and I couldn't find a flashlight. I did manage to find the furnace though.  I squirted some of that cheap vodka your sister sent in there, threw in a match and hoped for the best.}\\


\enquote{Seems to be working,} I stammered through now chattering teeth, \enquote{I can feel the heat coming through.} I held my hands up to the metal pipe that wound its way around the house.
\enquote{Keep the basement door closed. It's freezing down there.}\\


One of our favorite things to do when staying at a cabin is to read through all the journal entries of the previous guests. Usually, it was just things like \enquote{Went fishing with the kids, caught a bass} or \enquote{had a BBQ, played cards with the family}, but occasionally you found something more interesting, like \enquote{got drunk, set a tree on fire.}\\


We found the Paradise Pine diary and snuggled up on the couch. Aaron read aloud the first four or five entries before I decided to take over. We were about halfway through the book when we called it a night and went to bed.\\


The following evening we stayed up late as we had had a long nap that day. The plan had been to go on a hike but it had been too cold out. Luckily, the furnace in the basement was, to our amazement, still burning. We spent the whole day lazing around the living room. After dinner, Aaron practiced pool while I read aloud from the journal, starting where we had left off. I read for an hour before finally arriving at the journal entry of the guests who had stayed before us. I was very interested in this one; these people had to have a good story. 
The writer had chosen to format his entries into dates with time stamps. There were over 6~pages and I could already tell the handwriting sort of disintegrated as the days wore on. \\


\enquote{Wow, they must have been drunk ALL weekend, look at how messy this handwriting gets!} I held the book up to Aaron.\\


\enquote{Can you read it?} He asked, spinning the 8 ball into a corner pocket.\\


\enquote{Of course! I'm great at reading other people's shitty handwriting by now.} I sent him an impish grin and took another sip of wine before beginning to read.\\

\hrule

\textbf{Sunday, Nov 4th   3:30pm}
\\


Wow, what a beautiful cabin! My wife and I booked this place for two weeks on a whim and we can't believe how lucky we got! Barely made it back here with the truck, there's snow everywhere. At least a foot deep. And it's below 40~degrees outside --- thankfully the furnace in the basement is HUGE, as promised by Marissa, so all three floors are warm and cozy!\\


\textbf{Monday, Nov 5th 11:30am}
\\


We're snowed in! We had wanted to run home today to grab a few things we forgot but that is definitely not happening. The road is unmanageable so it appears we aren't going anywhere. Looks like we will be spending most of our day inside drinking mimosas and playing poker. As you can see, we aren't too upset about it!\\


\textbf{Tuesday, Nov 6th   7:25pm}
\\


My wife Sarah is currently cooking up a delicious roast chicken and I'm finally going to start writing. This is the reason we came here, after all, and I refuse waste the opportunity to cure my writer's block. It's just so gorgeous here I haven't written a damn thing! 
I also saw someone walking around the treeline today. I have no idea how they are surviving out there, we won't even go outside! It was 34~degrees last I checked.\\


\textbf{Wednesday Nov 7th 9pm}
\\


Today Sarah and I made a snow man and snow angels! We don't get snow in Scottsdale, so we are taking full advantage of it. I haven't been able to write anything new, but I did edit the previous two chapters of my book.  I think the beauty of this place is just too distracting. I'm kidding! (Sort of).\\


I think we may have neighbors. I was having a cigarette out on the balcony last night and I saw someone at the treeline again. He is extremely tall.  And certainly close enough to say hello but when I waved he walked back into the woods. Will have to ask Marissa about this? She didn't mention any neighbors nearby.\\


\textbf{Thursday Nov 8th 1pm}
\\


This morning I woke up to find animal tracks all around the outside of the cabin. I don't know what sort of animal made them. The prints were the shape of a rectangle, almost like they were made by the end of a $2 \times 4$. By the time Sarah got up at~11, the snow had mostly melted but you could still kinda see them. I think last night's snow is the last we will get while we are here. The sky is looking pretty clear. Sarah thinks I am succumbing to cabin fever, so today we are going for a hike since it's so beautiful out.\\


\textbf{Friday Nov 9th 7am}
\\


Last night someone tried to get into the house. I woke up at about 1 in the morning to the sound of banging on the front door. Not knocking, banging. I went downstairs and grabbed a pool stick. I asked who it was and the banging stopped. I waited a few minutes and then opened the door but there was nothing there. I started back up the stairs to wake up Sarah, as she is a heavy sleeper. The banging sounded again, more urgently this time, and from the other side of the room, on the wall next to the bookshelf. It stopped after a long minute and I sat down on the steps and waited all night for them to try something. Nothing happened after that.\\


\textbf{Friday Nov 9th 2pm}
\\


I told Sarah what happened and she wants to leave. I'm not really convinced, but Sarah scares easily. I will admit that I'm a bit on edge. I tried to start the car this morning but nothing happened. I'm not a car guy and I have no idea what to do. We can't hike out, there's no signal out here and we can't find a house phone. We talked about it and decided we're just going wait it out here. I know people have this cabin rented out on the 16th so we'll just have to wait the week for them. I did find a wood axe which I'm keeping in the bedroom, just in case they come back to harass us. I think it's probably a homeless person living out in the woods. There were tracks around the house again this morning and I'm no longer convinced they're from an animal. We'll see if they come back.\\


\textbf{Saturday 5am}
\\


Last night the knocking was back. But it was something knocking on the sliding door to our bedroom --- from the second story patio. I don't know how it climbed up there. It knocked on the window, gently, almost coaxingly. A thin curtain covers the sliding glass door so I couldn't see what it was. The knocking finally stopped and a full minute later it started again, becoming the loud, insistent banging of the night before. I reached over Sarah and grabbed the axe, bounding out of bed as she screamed. By the time I got to the sliding door the banging has stopped. I threw back the curtain but there was no one on the patio. In the moonlight, I saw it walking away from the cabin, back toward the treeline. Sarah stumbled over to the window and I showed her the retreating figure. She covered her face and cried. What we saw terrified us both. \\


It's not a human. It's tall, maybe 10~feet, and skinny. It looks like a black stick figure, impossibly thin. It has no hands or feet just stumps. And no face. It's just a black oval, with no features. The contrast was horrifying, this tall, black stick man walking through the snow. It reached the treeline and disappeared. I spent the next hour trying to calm Sarah down. She said we need to leave. I think she's right. When we were finally calm enough to lie in bed again, the silence was deafening. I felt myself slowly start to drift off. It was out of this silence that the knocking came again --- this time on our bedroom door. I jumped out of bed and grabbed the axe again. Sarah backed into a corner and screamed. By the time I threw open the door the knocking had stopped and there was nothing there, but the front door was wide open. It can get inside the cabin.  I don't know what it wants. \\


\textbf{Saturday 5pm}
\\


I am terrified. My wife is terrified. Today I considered setting the car on fire, just to see if the smoke would attract someone's attention. Sarah wouldn't let me because it's our only way out. So we packed the car up instead. Maybe when the snow melts more, we'll be able to fix the car. I catch Sarah staring off a lot and she hasn't said much since she saw the stick man. Seeing the thing, it's affected me too. I have been having migraines today. I've never had a migraine before. I want to protect my wife but I don't know what to do. I caught Sarah staring at me, almost in a trance earlier. I asked her what was wrong and she said \enquote{It eats us.} She seemed to snap out of it pretty quick after that and asked me why I was staring at her. She doesn't remember saying it and we can't figure out what it means. This thing is fucking with our heads. \\


\textbf{Sunday 10am}
\\


Last night I stayed up all night. It's lightly snowing. All was quiet.\\


\textbf{Sunday 7pm}
\\


I found footprints this afternoon on the upstairs balcony. The same rectangle ones the stick man makes. He was outside our window again. I brushed them away before Sarah could see. It stopped snowing an hour ago and its twilight now. I can see him in the treeline. I saw him turn around and walk back into the woods. His profile is as thin as a piece of paper. The stick man came back, though. I think we're going to die here.\\


\textbf{Monday Nov 12th  9am}
\\


Last night I went out on the balcony at around 8 for a cigarette. I heard a noise behind me and turned to see the stick man on the roof, 5~feet above me. I ran back inside to grab the axe and screamed at Sarah to arm herself. I turned around to run back outside and heard the stick man running above me on the roof, in the same direction. When I got outside, the thing was gone. I saw it running off into the trees again. But it was different. It was taller. I think there's more than one. 
When I got back inside, Sarah had locked herself in the upstairs bathroom. She was hysterical and kept saying she was going to die here. I tried to give her the pool stick but she wouldn't open the door for anything. I sat on the bed and waited. At some point Sarah must have fallen asleep because all was quiet. It was then that I first heard it walking around in the kitchen. I backed away from the bedroom door, courage suddenly failing me. It was in the house. I waited for more sounds from the kitchen but none came. After a few minutes, I finally heard a thump. It was on the stairs. It was climbing the stairs.\\


Thump. Slowly, but loudly. Thump. I banged the bedroom door from my side and told it to leave us alone. Thump. Sarah was screaming again, sobbing. It could hurt me, but I would never let it hurt my family. It stopped when it got to the top step. I could feel it on the other side of the door. It didn't make a noise. I tried to think of a strategy that would give me the upper hand if it attacked. I finally decided that if I threw the door open, it would knock the stick man down the stairs. On the count of three I turned the handle and kicked the door. It swung open freely, and I saw the black stick man still down on the landing of the stairs, facing me. It was more than 10~feet tall. I was paralyzed with horror for several long seconds when it started running up the stairs at me without warning. I stumbled back into the room as fast as I could as I realized that death at the hands of the stick man was more than death. Worse than death. It ate you. It kept you.\\


It stopped at the top step and dipped it head through the door taking 2~steps into the room. It was just a tall black shadow. Almost more of a dense absence of light than a solid black. Realizing the axe was still in my hand I moved between the stick man and the bathroom door. I raised the axe to attack, and at that moment the stick man screamed. It was unlike anything I had ever heard before. I wanted to hold my hands over my ears as I felt an ebbing thunder in my brain. I heard the mirror shatter in the bathroom from the sound. I thought of Sarah. With the last ounce of strength I had I ran at the thing, axe high and brought it down in the creature's chest. Over and over again for what felt like forever but was probably no time at all. It threw me aside and I heard my wife scream. That's the last thing I remember before I passed out. \\


When I opened my eyes again it was mid-morning. My wife was gone. The bathroom door was gone. And the axe was gone. I looked for Sarah all morning; I walked deep into the woods. I searched for miles. I am going to sleep for a few minutes and then go back out into the woods to find her. I hope I meet the stick man. If Sarah is dead, I want to be dead too. I think that's what it wanted all along. \\


\textbf{Monday Nov 12th 6pm}
\\


It's getting dark and harder to search the woods. In my mind, all I hear is her voice. \textit{It eats us.}
 Over and over again. What has it done to her. \\


I couldn't save her. After everything, I couldn't save her. When I first realized I had forgotten my medication, the snowstorm stopped us from leaving. But when I saw the stick man I thought it had been a blessing in disguise. I needed to be clear-minded and alert to protect my family, and I couldn't do that when I was on the Haloperidol.  But it didn't matter in the end anyway. I couldn't save her.\\


The car started on the first try this morning. It's letting me leave.  I'm going to drive around to the other side of the mountain and walk back towards the cabin. Maybe I'll find the stream. Maybe I'll find Sarah. It would be useless to stay another day, the stick man is gone. I know it in my heart. And it's below freezing and the furnace has burned out, the firewood is gone. If I find her I'll come back and write in this book. My only friend, now.\\

\hrule

Aaron had stopped playing pool long ago and the wine hadn't been touched since I started reading. We stared at each other as the last line echoed around the cabin. We both seemed to wake from our paralyzed state at the same time. I threw the book across the room and Aaron backed up into the bookcase saying \enquote{Jesus!}\\


\enquote{This is fake, right?} I asked as I stood up. I didn't need the glass of wine anymore. I needed the bottle.\\


\enquote{I don't know, Linds, I don't\dots I don't think so.} \\


\enquote{The guy said he was a writer,} I insisted, \enquote{he probably just wanted to write a scary story for other guests. Although he really crossed the line into downright disturbing.} I took a sip of wine and turned around to see Aaron eyeing the stairs, warily.\\


\enquote{You can't be serious, Aaron. It's creepy as shit, I agree, but come on.}\\


Almost like he didn't hear me, Aaron started ascending the stairs. I don't know what he wanted to see up there, but I put the wine down and followed suit. By the time I got into the bedroom Aaron was sliding the glass door open. I followed him out onto the balcony. You could see the treeline from the patio very clearly. I searched the woods for any movement but saw nothing. I turned to say something to Aaron and found him studying the roof. He threw a wild look at me and walked back inside. I followed him in.\\


Aaron paced around the room.\\


\enquote{What?!} I was starting to get annoyed.\\


\enquote{It's all just like in the story. You can see the treeline, the field and the roof from the balcony. And look---}\\


He pointed to the attached bathroom.\\


\enquote{---there are hinges but no door. There should be a door, it's a bathroom. And the mirror---} \\


\enquote{What?} I interjected. \enquote{Was shattered by the stick man's scream?!} He was starting to scare me. Aaron was usually the most logical person I knew. \\


\enquote{The stick man? Did you even pay attention to what you read? There was no stick man.}\\


\enquote{No shit.}\\


\enquote{No, I mean, there never was. His last entry, about the medication --- and how they got snowed in and couldn't go back for it --- Haloperidol, it's used to treat schizophrenia. Lindsey, go read it again. The entire thing is him slowly succumbing to his psychosis, page by page. Hell, his wife knew it was happening!}\\


\enquote{This is madness, Aaron.} I walked into the bathroom and looked around. \enquote{You think someone died in here? Four days ago?}\\


Aaron shook his head. \enquote{I don't know. I think it's a possibility. The shower curtain is torn down, the mirror is broken. It certainly looks like there could have been a struggle in here. And the door\dots the axe\dots .both missing.}\\


The logic of his conclusions began to dawn on me.\\


\enquote{Oh my God, if this is real\dots  Aaron, we cleaned this place top to bottom when we got here. If there was a murder, we've destroyed all the evidence!}\\


\enquote{We didn't know. We didn't know that someone died here---}\\


\enquote{We still don't know.  Aaron, where's the body?}\\


\enquote{I don't know. Maybe it's buried out in the woods.}\\


\enquote{We need to leave; we need to go get help. Let's take the book to the police and tell them what we found when we got here. Just to be safe.}\\


\enquote{Okay. Okay, Jesus, this guy could come back anytime. Let's get out of here.}\\


We had just started down the stairs when another thought occurred to me. I stopped on the landing.\\


\enquote{Aaron\dots }\\


He turned around, \enquote{Yeah?}\\


\enquote{He said the fire in the furnace had burned out. Did you put firewood in when you lit it?}\\


\enquote{No\dots it was almost pitch black. I couldn't see any firewood.}\\


\enquote{But\dots We've been burning that furnace for almost a day.}\\


I could see the implication slowly dawning over Aaron's face.\\


\enquote{What have we been burning, Aaron?}\\


He ran for the basement door, and I followed. When he opened the door, I can't describe to you what came up from below. It was a hot, pungent, heavy air. I stood on the top step as Aaron descended into the basement.\\


\enquote{The axe is down here.}\\


I took a deep breath and followed him down. I stopped on the bottom stair, refusing to go any further. It was still very dark but for the light coming down the stairs and a soft orange glow in the back of the room. Aaron knelt in front of the stove door. He looked over at me and I nodded. Aaron slowly turned the handle and pulled open the furnace door. The fire inside lit his face and after moment, the horror expressed there told me everything I needed to know.\\

\hrule

They found Jason Harding less than a month later. He had hung himself out in the woods, 50~yards from the cabin. In fact, he had been hanging there when we pulled up on Sunday, the 18th~of~November. I've often wondered if he hung himself because he wanted to be with his wife, or if he hung himself because he realized what he had done.\\


I hoped it was the latter because I hated him so much. Not for his mental illness, not for his crime --- but for what he did to us. Sarah Harding had burned in that furnace for a day, and for a day, we had breathed in every atom of her body. We had kept warm by the flesh of her corpse. Why didn't it smell? We were given a very scientific explanation citing high burning temperatures, years of pine infusion, and the pieces of wooden door burning in there with her. But it didn't stop the nightmares.\\


The case made headline news, at least locally. Aaron and I managed to prevent our names being associated with Paradise Pine through an anonymity clause on our witness statements.  We never told our friends or families we were involved. We tried to forget. \\


Paradise Pine still stands today. It is available for rent, although the name has been changed. The owner insisted on keeping the cabin journal, so the police tore out Jason Harding's pages and gave it back to her. It still sits on the table next to the bookshelf, and tenants still read it and write in their own experiences. \\


I pity those people. They will wonder about the torn pages and never learn what was written on them. They will cringe at the door-less bathroom and never know someone was murdered there. They will light the basement furnace and never realize its dark history. \\


And they will never know that the quiet, charming, peaceful cabin they're staying in is actually the Paradise Pine.
\end{document}