\documentclass[a5paper]{scrartcl}
\usepackage{amssymb, amsmath} % needed for math
\usepackage[utf8]{inputenc} % this is needed for umlauts
\usepackage[USenglish]{babel} % this is needed for umlauts
\usepackage[T1]{fontenc}  % this is needed for correct output of umlauts in pdf
%\usepackage[margin=2.5cm]{geometry} %layout
\usepackage{hyperref}  % links im text
\usepackage{csquotes}
\usepackage{stackengine}
\usepackage{graphicx}
\usepackage{siunitx}
\def\asterism{\par\vspace{1em}{\centering\scalebox{1.5}{%\\
 \stackon[-0.5pt]{\bfseries*~*}{\bfseries*}}\par}\vspace{.5em}\par}

\usepackage{yfonts,color}
\usepackage{mystyle}
\usepackage{microtype}

\title{The Lost Town of Deepwood, Pennsylvania}
\author{C. K. Walker}
\date{February 11, 2014}

\hypersetup{
 pdfauthor  = {C. K. Walker},
 pdfkeywords = {},
 pdftitle  = {The Lost Town of Deepwood, Pennsylvania}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\\
% Begin document                                                    %\\
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%\\
\begin{document}
\maketitle

\begin{shadequote}[l]{horriddaydream}
Well, don't want to live in Pennsylvania anymore.
\end{shadequote}

\begin{shadequote}[l]{splkennedy}
That was really good! I have to admit I often scan to the bottom to see how much is left to read\dots didn't do it once with this. Creepy story and really well written. I could see everything you described!
\end{shadequote}

\begin{shadequote}[l]{phyve}
Sorry to tell you, but this isn't the first incident of something like this. There was a similar incident of a town vanishing in Kansas,~1952. I understand this may be troubling, but there is more to this story.
\end{shadequote}

\yinipar{\color{black}W}hen I was a kid my dad traveled a lot for work. Back then, his company was growing exponentially and my father was sent to oversee the opening of new stores all across the country. In~2002, he had a particularly busy year. My dad was assigned to a store in Pennsylvania and, because it was a longer assignment and because it was summertime as well, he decided to take my mom and I with him. \\


Since we were going to be there for two months, they gave us a fully furnished house in the suburbs. It was two stories tall and at the end of a very lonely cul-de-sac. The town itself was very small, with a little over $\num{3000}$ residents, and the suburb where we stayed was even more rural.  \\


Our neighborhood was relatively new, and most of the houses were still empty. The housing development, Lone Wood, had only just started cutting into the dense forest that surrounded it and all the empty houses gave it a very eerie, albeit boring, feel. \\


Lucky for me, there were a few other kids who lived in Lone Wood and one of them happened to be my age. Jamie and I were both 12 and really that was all we needed to have in common. \\


We had a lot of fun that summer. Being a city kid, I was eager to explore all the bike trails local kids had made out in the woods. The city of Middlesbrough was a very old town which was incorporated sometime in the early 1800s. The town had tons of history, but nothing really to do. One particularly boring Sunday, Jamie and I even went to the town's museum. \\


It was pretty boring, as expected, until we heard some kid ask an employee about the \enquote{lost town}. The employee replied that that was just a legend, but that was enough to pique my curiosity.\\


I quizzed Jamie about it but he didn't seem to know much either. It was a full five weeks into the summer before I finally got my questions answered.\\


Jamie and I were building a bike ramp over a narrow stream late one afternoon when we saw a group of five teenagers boisterously heading out into the woods. They were carrying flashlights and beer, several of them trying to scare the girls of  the group into turning back.\\


\enquote{I wonder where they're going.} I mused as I glanced over at Jamie. He stood up and wiped his brow. \\


\enquote{I know where they're going.}\\


\enquote{Where?} I stood up and dusted the dirt off my shorts. The novelty of living in a small town had weeks ago given way to boredom and I jumped on anything that sounded remotely interesting.  \\


\enquote{They're looking for the Lost Town.} He sighed regretfully.\\


\enquote{Okay, seriously, what is that? I knew you know more than you let on. I need to know Jamie, I need to know!} I shook his shoulders in mock hysteria and he stumbled for balance.\\


\enquote{ Alright! I'll tell you, geez, Katie!} Jamie picked up his bike and started walking down the bike path. I grabbed mine and followed him.\\


\enquote{The Lost Town is just a dumb legend.  The stories say that Middlesbrough had a sister city nearby, somewhere out in these woods. Then one day, like a century and a half ago, the whole town just disappeared. The people left or died, nobody knows, nobody even remembers the name of the town. It's like a right of passage or something for kids to go looking for it.}\\


\enquote{Jamie we should---}\\


\enquote{No!} He stopped and turned to look at me. \enquote{Some kid went looking for it in the~70s and never came back. They found his body like ten years later in the middle of nowhere. He got lost out there. It's easy to do, everything looks the same.}\\


\enquote{He was a total idiot! Probably on drugs, it was 70s. We are a totally different generation --- we have satnav!}\\

\enquote{Satnav?} He looked at me curiously. Jamie had lived in this 
town his whole life and sometimes I forgot how sheltered he was.\\

\enquote{Satellite Navigation? My dad has a GPS that he totally wouldn't notice missing for a day. Come on Jamie, it'd be so much fun!}\\


\enquote{I'd better get back.} Jamie looked at his watch and then mounted his bike. \enquote{My dad is taking me to a movie tonight.} \\


We rode in an uncomfortable silence until an idea struck me as we rolled over the abandoned train tracks. They were old and almost buried by plant growth. \\


\enquote{Hey\dots I know you don't want to talk about it, but has anyone ever found anything?}\\


\enquote{No. Well, my friend's older brother said he found some human bones out there once, but nobody believed him.}\\


\enquote{Oh. And where do people look?}\\


\enquote{Well, almost everybody goes to the lake.} He pointed to the left of us, where we'd seen the teenagers heading earlier. \enquote{It's pretty deep back there but they figure that if there was another town, they would have lived by the lake, so\dots that's where they go.}   \\


\enquote{Well, you know what I would do? I would follow the train tracks. I mean, they look pretty old. And I don't know why they would lay them going back into those woods unless there was something back there, so that's where I'd go.}\\


Jamie considered this and then nodded. \enquote{Yeah, I guess I could buy that. No one follows the tracks that way, though. That's where that kid that disappeared went.} \\


I wasn't swayed.\\


I didn't bring up the Lost Town again until two weeks later. It was the weekend before we were moving home and my parents had a barbecue for the employees of dad's new store and some of our neighbors. Jamie and I hung out inside the house and played my N64 while we flirted pretty outrageously. There had been an unspoken sort of mutual attraction throughout the summer that no one had had the guts to act on. Since I was moving home in five days, there really was nothing left to lose. \\


Although his intentions were probably pure and genuine, I am embarrassed to say that mine were not. I thought that if I could make him want to impress me, he would agree to go looking for the Lost Town. The legend had thoroughly consumed me. I had been to the local library every morning for the past week looking for more information on the town and had found nothing. But legends don't just come from nowhere! I was sure of it.\\


I knew if we didn't leave by 2~p.m. we wouldn't have enough daylight to carry out my plan. I already had a backpack packed with water, a flashlight, a camera and a can of red spray-paint. I figured if we left the tracks we would need a way to find our way back to them. I thought I was so clever. \\


Nothing in that backpack made a damn bit of difference in the end. I was a fool.    \\


I set my controller down and turned to look at Jamie. \\


\enquote{So\dots do you want to go out to the woods one last time?} I raised my eyebrow at him and smiled. \\


\enquote{Yeah!} He said excitedly and he jumped up off the couch. Then, embarrassed, he cast his eyes down at the floor. \enquote{Yeah, you know\dots if you want to, that's cool.}\\


\enquote{Cool, let's go!} I grabbed his hand and ran out the front door, grabbing my strategically placed backpack on the way. Jamie didn't even notice it; he was walking faster than I was.\\


When we had gotten a decent way into the trees, Jamie turned around and looked briefly at my face before casting his eyes to the ground. He rubbed the back of his neck.\\


\enquote{I've actually, like, wanted to kiss you all summer.}\\


I was stunned to silence, absolutely dumbfounded that Jamie had found the guts to say anything like this. I knew I needed to fill the awkward silence left in it's wake, so I did the only thing I could think of --- I leaned in and kissed him. \\


It was the awkward first kiss of two twelve year olds, but it made me feel warm and sent a flight of butterflies swirling into my stomach. So I actually really did like Jamie. How about that?\\


I let him go and his face was the same shade of red that I imagined mine was. He quickly changed the subject to how long he'd wanted to ask me out but that he didn't think I liked him back. We walked for awhile carrying on this conversation, him oblivious to his surroundings, me subtly leading the way. \\


It took him stumbling over the tracks to break off his monologue and finally notice the backpack. He looked at me like I'd punched him in the face.\\


\enquote{You can't be serious.}\\

\enquote{Jamie, I know but look, this is the last time I'm going to see you in a really long time and I want to remember today! We will only be out for two hours max; we'll be back before they even realize we're gone!}
Jamie stared at the tracks for a minute and seemed to be considering it all. I held my breath until he finally let out a deep sigh.\\

\enquote{Okay.}\\


\enquote{Oh my God, Jamie, I---} He held up his finger, cutting me off.\\


\enquote{But we follow the tracks the entire time and we turn around after an hour.}\\


\enquote{Okay!} I was so excited that I hugged him. It would be the first and last time I ever did.\\


As we walked, we talked about all sorts of mundane things, stopping only to make sure we were still on the tracks. It felt like we had only been walking for 45~minutes but when Jamie checked his watch, it had been 3~hours.\\


\enquote{That's weird\dots it hasn't been 3~hours. It says its 5~o'clock.} He trailed off.\\


\enquote{I swear, we left just after~2. It's can't be 5, dude, your watch is busted.} I gave him a playful shove.\\


Jamie raised his eyebrow at me and smiled. \enquote{Even so, we should probably turn around. }\\


He wasn't wrong, the sun was setting. The shadows were long and looking around, I wondered if it really was 5~o'clock. \\


But I wasn't ready to give up just yet. As we had been walking, I'd noticed something taking shape off of our right; a large mass, maybe a quarter mile away. It was denser than the area around it and seemed to have clean, man-made lines. \\


\enquote{Jamie, look.} \\


He turned. \enquote{Yeah, I was hoping you hadn't noticed it. It's a long way off though; we would never find the tracks again.}\\


\enquote{Yes, we would, check it out!} I triumphantly pulled the spray paint out of my backpack. \enquote{It's for the trees.}\\


He took the can and shook it, then made an experimental ‘x' on a nearby tree. \\


\enquote{OK, but I get to do the spraying.} I didn't argue.\\


The closer we got to the mass, the more it took shape. First we could tell it was a building. Then we could tell it was church.  By the time we got the front door, we were looking at a very old and dilapidated chapel. Remembering my camera, I took a picture of the wooden plaque over the door; whatever had been written on it had long ago worn away. We walked around the church in awe. The building was small, maybe 500~square~feet. The windows were, surprisingly, all in tact but were so caked with dirt and grime that we couldn't see anything inside. \\


\enquote{How do we get in?} I asked quietly.\\


\enquote{I don't know, but we're going to figure it out! Wait until my brother hears about this. I mean, holy shit. Look at this place!} His excitement was contagious.\\


The front door had a pull handle but try as we might, we couldn't seem to open the door. \\


\enquote{Do you think it's locked?} I asked as I watched Jamie struggle with it.\\


\enquote{Yeah, maybe. I mean it must be. There was a door around back, though.}\\


The door at the back was a lot more sympathetic and let us in with relative ease. We were standing in a small room with an old wooden desk attached to a wall. There was a small fire place and old portraits hung up around the tiny office. The people in the pictures were all standing in front of the same maroon background and were looking down at us disapprovingly. Books were scattered everywhere, most in a language I had never seen before. The floor was covered in dirt and a pair of old shoes were laying haphazardly in one corner.\\


\enquote{Whoa,} I said in awe.\\


\enquote{Yeah, whoa.} I looked over at Jamie who had a huge smile on his face. He was holding up a cross and a piece of paper.\\


\enquote{What is it?} I walked over to see.\\


\enquote{It's a list of names. There's like 60~people on this list. Maybe a town census?}\\


\enquote{Let me see.} I pulled my flashlight out of my backpack and shined it on the parchment. \\


\enquote{Deepwood. Do you think that's the name of the town? All these names are crossed out. All except this one.} I pointed to a name at the very bottom. \\


\enquote{Maybe it was the plague.}\\


\enquote{You think it's a list of the dead?}\\


Jamie shrugged. \enquote{Makes as much sense as anything else.}\\


I walked over to the desk and leaned against it. \enquote{Why do you think they left? I mean, look, there's a jacket or something on that chair, and shoes over there. The town pastor or whatever, he just took off and left everything like this?}\\


\enquote{Or died, }said Jamie as he folded the paper and put in into the back pack. \\


\enquote{Yeah, died\dots either way it must have been creepy as hell to be alone in here.} I stared at one of portraits for several long seconds; the young woman painted there seemed to be staring down at me with a very accusatory look. It made me incredibly uncomfortable. \\


I was so absorbed in the paintings that I didn't notice the slow creaking from overhead until the ceiling cracked loudly as it started to cave in. I screamed and covered my head, but the next thing I knew, I was lying on my back over the threshold of a door, Jamie on top of me protecting his head. \\


\enquote{Ah, thanks,} I mumbled as I gently pushed Jamie off of me. \\

\enquote{Don't mention it.} Jamie climbed to his feet and brushed himself off.
I glanced behind him at the office, which was now filled floor to ceiling with decaying debris.\\

\enquote{Jamie, that was our way out.} \\


\enquote{That's OK. We can unlock the front door now that we're inside. Or break one of the windows.}\\


If the back office was unsettlingly, the chapel was downright disturbing.\\


Even though the grimy windows allowed very little sunlight in, I could make out eight rows of pews lining a narrow aisle and a tall podium at the front of the chapel.\\


Jamie and I stumbled around the small nave breaking windows on either side with pieces of wood we had found. The sun was still setting and I wondered how much of a difference the muted light would make. When I broke the last window on my side I turned back around to survey the chapel, disappointed that the lighting wasn't much better. The room itself seemed to repel light.\\


The wooden pews were completely rotted. In fact, the wood we had used to break the windows of the church were leg stands from the front row. The narrow aisle in between the rows of pews was littered with leaves and rotting wood. But that was nothing, nothing compared to what sat upon the alter. \\


It wasn't a podium, as I had thought earlier. It was a statue of the crucifixion – but unlike any I had ever seen before. The paint had been worn away on every part of the statue – except the blood of the crucifixion wounds, which stood bright and realistic, and seemed to be oozing before our very eyes. The only other surface left untouched by the decay of time was the face of Jesus. The details of his face were still so incredibly minute and perfect, and he had the same accusing eyes as the portraits in the pastor's office. He seemed to be staring directly at me and I could tell Jamie felt the same, though he was across the room from me. \\


The statue's stare awarded me an edge of panic, and I suddenly realized that we needed to leave. We weren't wanted here. I had the sudden feeling that we were trespassing on some sort of hallowed ground. We had found the church, we had documents proving we had been here – and now it was time to go. \\


I turned to Jamie to tell him so and could immediately tell that he did not share my feelings. He had been born and bred on these legends and nothing was going to tear him away from our discovery. I watched him walk over to grab the camera out of my bag. He took pictures of everything he deemed interesting, including the crucifixion statue, much to my unease. \\


I gave him several minutes before I said something.\\


\enquote{Jamie, I think we need to leave.} I said in a low voice.\\


Jamie stopped and looked up, seeming to remember I was there.\\


\enquote{Are you kidding? This is what you came for! We have to bring home evidence, of all of it.}\\


\enquote{It's going to be dark in half an hour. It's already hard to see in here\dots}\\


\enquote{Duh, that's why I'm using a flash. Hey, can you get a picture of me next to this creepy Jesus thing?}\\


\enquote{Um\dots I guess,} I mumbled as I took the camera from him. I didn't even want to look at it, much less photograph it, but if it would help me get him out of here I was going to stomach it. \\

Jamie wrapped his arm around it just as I snapped the picture.
\enquote{Don't touch it! Oh crap, why did you touch it? There's something off about that thing, Jamie. Can we fricking go now?!}\\

\enquote{Yeah, fine.} Jamie walked over and picked up the backpack as I headed toward the front door.\\


I noticed there was no lock on it. I pushed against the door as hard as I could --- it didn't budge. My heart sank; there wasn't even a handle or a knob. It was just a solid piece of wood with strange markings on it. Symbols I had never seen before. \\


\enquote{Jamie, the door is stuck,} I said as I turned around to see him testing a piece of the floor with his foot.\\


\enquote{What are you doing?} I asked, hearing the edge of panic in my voice. He was still at the front of the chapel, a foot from the Jesus statue hopping back and forth from one part of the floor to another. The statue's eyes seemed to be only on him now.\\


\enquote{There's something under here. See?} I heard the floorboard creak under his left foot as he put weight on it. \\


\enquote{Jamie, don't.}\\


\enquote{No, it's like, under the dirt right here, the floor is hallow,} he kneeled down and starting digging through the thin layer of dirt, \enquote{it's like a trapdoor or something!}\\


And it was indeed a trap door. By the time I had walked the length of the pews, Jamie already had the edges dug halfway out.\\


\enquote{Let's just leave it and your brother and his friends can come back and see what it is, please, Jamie, I want to go.} There was something wrong with this place. Terribly wrong. And the thought of spending one more minute here had me on the precipice of a panic attack, something I hadn't experienced in over a year. \\


I sat down against the front pew and put my head down. I heard a roaring in my ears and my breathing grew labored. I had to leave here, even without Jamie. I rocked back and forth for a few minutes as I tried to calm myself down. I would climb out a window and run – in any direction, it didn't matter.\\


\enquote{There's something here, under the church.} Jamie's voice sounded a million miles away.\\


By the time I pulled myself together enough to lift my head, Jamie was knelt next to me.\\


\enquote{I didn't know you were claustrophobic.} At least, that's what I think Jamie said. I better remember the horror I felt as I stared at the hole in the floor. Jamie had opened the trap door.\\


\enquote{Two minutes,} Jamie said as he stood up. \enquote{We go down, we take a couple pictures of whatever's down there and we come right back up and leave. Just two minutes, Katie, that's all I'm asking.}\\


I wanted to say no. I intended to. But I felt myself slowly nodding as Jamie pulled me to my feet. To this day I don't understand why I agreed. But I suppose that it's better that what happened down there didn't happen to Jamie alone.\\


\enquote{We're going to come back with the story of a lifetime! What if there is valuable stuff down there or something? Old shit is always worth money. We could be rich! So rich that your family could stay here. You could buy the house you're living in and come to school with me in September.}\\


I managed a small smile. Of all the things someone could think to buy with wealth, Jamie's first thought was to keep me here with him. And he was right, there could be anything down there and almost all old stuff was valuable. I took a deep breath.\\


\enquote{Okay, 2~minutes,} I agreed.\\


As we leaned over the trapdoor and peered down, the first thing we noticed was an intense heat emanating upwards from the hole. The second was the strangely out of place spiral staircase leading into the depths below. \\


Jamie rolled the flashlight over to me with his foot and I picked it up as he pulled his lighter out of his pocket.\\


\enquote{Ladies first,} he smirked at me.\\


I stared at him slack jawed. \\


\enquote{No way. You found this door, YOU go first. Between the black staircase and the heat, I feel like we're descending directly into hell. I am not going first.} I crossed my arms and glared at him to reinforce my point. \\


Jamie simply shrugged and stepped onto the staircase. \\


I took several deep breaths as I watched his head disappear into the darkness below. I almost didn't follow him. I was still deciding when he yelled at me to shine the flashlight down the stairs so he could see. \\


I started down the stairs after him. They went down much farther than I thought, and it became warmer and warmer the further down we went. \\


When we finally reached the bottom, I was holding back what threatened to be a massive anxiety attack. We were farther beneath the church than I thought we'd be and it was hot, muggy and difficult to breathe. \\


Hoping to get this over with as fast as possible, I swung the flashlight around the chamber hoping to reveal its hidden treasure. What I saw there, I can never describe, though I have tried many times. \\


The room was entirely empty, save two things. One was a desk in the corner, much like the one in pastor's office. The second was another statue. \\


This one was roughly twelve feet tall, and remains to this day the most terrifying thing I've ever seen. To put it mildly, it was some sort of demon. It towered over us and as such I could only see the bottom of its jaw from where I was. It was looking directly ahead of it, at the staircase we had just descended. Its tail was long and swept around the entire room. There wasn't a lot of room to move. It had claws, like any modern depiction of a demon and as I moved around the chamber to view its profile, I noticed it had horns as well. \\


Neither Jamie nor I spoke as we shuffled around room, our backs to the wall as far away from the demon as physically possible. I stepped carefully over the tail as I made my way to its back and came around to the other side of the statue. \\


I couldn't take my eyes from it, I couldn't trust it. If the statue upstairs seemed to bleed, what could this one do? As I eyed the talons on the gigantic stone feet, Jamie broke the silence.\\


\enquote{Can you even believe this shit?} His voice was coming from the other side of the room. I searched the darkness for the weak glow of his lighter and was relieved to see it moving towards me. I turned my flashlight upward to shine it on the side of the demon's head. The horns had to be at least a foot tall. As I brought it down to see where Jamie was, I hit my arm on something hard.\\


\enquote{Ow, my head!} Jamie squeaked as my flashlight fell to the ground and rolled under the desk.\\


\enquote{Goddammit, Jamie,} I whispered in a panic. I dropped to my knees and felt around under the desk, searching for the flashlight. \\


\enquote{What! It's not my fault you cracked me on the head.} \\


I stood back up and swung the light around to see Jamie trying to relight his lighter – but it wasn't him that stopped me dead. \\


I will forever be frozen in that moment. I don't know why I couldn't speak, couldn't scream, couldn't move. All I could feel was my own intern decent into madness.\\


As I had moved the beam of light up to Jamie's face I had seen another face right next to his. A twisted, angry, soulless face – the demon's. The statue had bent down and turned to the side; its head mere inches from Jamie's. And it was staring at me. I can not describe its face, and I am not sure my mind will ever let me remember it in detail. \\


It shook me to my core in a literal sense. My body was having a dark, violent, visceral reaction to this impossibility. Jamie finally noticed the flashlight shaking in my hand and turned to see what I was looking at. \\


It wasn't until he started screaming that I was shaken from my paralysis – I dropped the flashlight, Jamie dropped everything else, and we ran.\\


We took the stairs 2 and 3 at a time, Jamie pushing me up ahead of him. Halfway up I slipped and we both went tumbling down halfway to the bottom. In that horrible moment we heard the grinding of stone against stone and we knew the statue was moving. Jamie screamed but I was mute, too horrified to make a sound. We got up and kept climbing, never taking our eyes off the small, dying light above us; our only salvation now.\\


We were almost to the top when we first heard it on the stairs. It was so large and heavy that the entire staircase shook with the impact. Terrified that the stairs would come crashing down and we would be left alone with it below, we jumped the last 3~steps.\\


Jamie pushed me up out of the opening. He climbed out after me and tried to slam the trapdoor shut but it was somehow stuck.\\


We could hear a deafening thunder on the staircase as the statue slowly climbed the steps. I helped Jamie try to push the trapdoor closed and for the first time noticed the symbols on the bottom of the wood – the same as those on the front door.\\


Before I could begin to comprehend this, I noticed the demon first penetrate the shaft of light on the staircase below. It was coming. Jamie saw it too and pulled me to a standing position while pointing at the front door.\\


We both ran at it as hard as we could – but when we hit it, it didn't budge. We tried again, but it was unsympathetic.\\


\enquote{Katie, the windows!} We ran to the closest one and tried to climb up the wall to get out, but the windows were too high.\\


The thunder from below was getting louder, closer. It was more than half way up the stairs\dots\\


We tried to climb on the rotting pews to reach the windows but they crumbled under our weight.\\


\enquote{I'll push you out, give me your foot!} Jamie yelled over the sound bellowing from below.\\


I shook my head. I wanted to, God, I wanted to. But I couldn't leave him. I couldn't leave Jamie to face that thing alone. We both looked over at the door again. Our only chance was to keep trying to break it down. We stumbled back into the aisle and ran at the front door with everything we had. I thought I felt it move. We backed up even further and ran at it again. This time the impact knocked me backwards into the aisle and Jamie barely stayed on his feet. He looked at me in horror and I turned around the see stone horns rising up from the darkness of the trapdoor, 3~feet from where I sat. \\


We were going to die here. I stood up, refusing to turn around again. I knew that the next step it took would bring its head into the room, and the thought of seeing it's face again had me running at the door with every last bit of strength I had. Jamie reached it at the same time and I felt it give way as we crashed through the threshold and landed outside the church.\\


Jamie had picked me up off the ground before I could think to move and we were running toward the train tracks at an Olympic sprint. We could still hear the thundering on the stairs no matter how far we got from the church; every step echoed through the woods like a gunshot – until they stopped. It was here.\\


I had no idea if we had run in the right direction or if we would be forever lost in those woods. It was now dark outside and the temperature was dropping fast. I was beginning to panic that we would never find the train tracks when I noticed Jamie wasn't next to me anymore. I turned around in a panic to find him sprawled on the ground a few yards behind me --- he had tripped over one of the rails. He was up and running down the tracks before I could even ask if he was okay. We ran until we couldn't anymore.\\


Our running eventually slowed to a jog and the jog to a walk. We hadn't spoken – neither of us had any idea what to say – and it wasn't until we had both gotten our breath back that one of us finally broke the silence.\\


\enquote{How long have we been on the tracks?} Jamie's voice had an edge of barely suppressed fear. I looked at his wrist, and noticed his watch was missing.\\


\enquote{It didn't take us this long to get, to get\dots to find that place. Or did it? Do you think maybe we went the wrong way?} Jamie asked hesitantly.\\


I couldn't afford to think like that. If we had somehow gotten turned around and ran the wrong way down the train tracks, than we were deeper into the woods than ever.\\


\enquote{No. We went the right way,} I said to convince myself.\\


\enquote{That thing,} Jamie started, \enquote{I thought it was a statue. But maybe it was some crazy undiscovered giant reptile that was, like, hibernating and we woke it up.}\\


So we were going to delude ourselves into thinking that there was a scientific explanation for this. I understood why but I just couldn't accept it.\\


\enquote{Yeah,} I said slowly, \enquote{did you, um, did you see the weird writing on the front door? It was on the trapdoor, too. Do you think it was keeping it down there? Because, Jamie, all those doors are open now.}\\


\enquote{Well, if it's an animal, words mean nothing to it, anyway.}\\


\enquote{Yeah, if\dots} I trailed off hoping he would challenge my implication. He didn't.\\


I could tell this was something Jamie's mind wouldn't accept. But he hadn't seen its face, not like I had. It was no animal. It was made of stone. It was something sinister and anciently evil and it had seen me, had seen right down into my soul. It was aware of me and I was aware of it. And now, it was free. Whatever had been keeping it beneath the church has been awkwardly destroyed by Jamie and me. That thing was free to walk the woods and go God knows where. \\


We walked in silence for another half hour until Jamie suddenly stopped short and started yelling.\\


\enquote{Here! We're here!} He booked it down the tracks toward a swarm of flashlights and I followed close behind him. As soon as Jamie reached his parents he collapsed, while I ran into my mother's arms and cried like a child. I couldn't hold it together any longer.\\


The police report says we were found at 4~a.m. – by our sense of time about 3~hours after the sun had set. We had spent less than an hour in the chapel and yet we seemed to have lost 10~hours there. We never told anyone where we had actually been, or that we had found the lost city of Deepwood. We simply said we went for a walk to the lake and got lost in the woods. \\


My family left Middlesbrough the following Monday – two days ahead of schedule. My father had another store to open and there was really no reason to wait. Jamie didn't come to say goodbye to me and after we left Middlesbrough I never saw him again. I kept a copy of the police report to remember him.\\


Over the following year, Middlesbrough slowly disappeared. At first, I could just feel the memory fading unnaturally from my mind. My parents couldn't remember that we had ever been there, which scared me more than anything else. I taped the police report to the ceiling over my bed so that Jamie would be the first and last thing I thought about everyday.  \\


Then, the Middlesbrough city website disappeared as did that of the local paper and the town's two public schools.\\


The store my dad helped open in 2002 also disappeared from the company's website. After that I could never find any mention of Middlesbrough anywhere online ever again.\\


Over the years, I searched public records for Jamie's full name and found nothing. I hired someone to illegally search private records and he came up empty too. In the end, the only proof that Jamie ever existed at all was the police report with his name on it.\\


And then nothing was left.  One day the paper I had had taped to my ceiling for so many years was blank. I remember what it was and what it looked like before, but now it's just an old weathered piece of blank paper.\\


All that remains of Middlesbrough and the people who lived there are my memories. And this is why I am writing this story down and uploading it to the internet. Once it's on the internet, it can never die, right? Or perhaps one day it will just disappear and you won't remember ever seeing it and I won't remember ever writing it.\\


And I can only hope that this ended with Middlesbrough. If it has moved on to other towns, who would know? Who would even remember? \\


I wish I had answers. But all I have are questions.
\clearpage
\section*{Stories of this series}

\begin{itemize}
    \item Story~1: The Lost Town of Deepwood, Pennsylvania
    \item Story~2: Return to Deepwood, Pennsylvania
    \item Story~3: Death of Deepwood, Pennsylvania
\end{itemize}
\end{document}